### 2024-11-05 arxiv/paper.tex
mac

\documentclass[10pt,a4paper,onecolumn]{article}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{tikz}
\usepackage{hyperref}
\hypersetup{colorlinks,breaklinks=true,
            urlcolor=[rgb]{0.0, 0.5, 1.0},
            linkcolor=[rgb]{0.0, 0.5, 1.0}}
\usepackage{caption}
\usepackage{tcolorbox}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{seqsplit}
\usepackage{xstring}

\usepackage{float}
\let\origfigure\figure
\let\endorigfigure\endfigure
\renewenvironment{figure}[1][2] {
    \expandafter\origfigure\expandafter[H]
} {
    \endorigfigure
}

\usepackage{fixltx2e} % provides \textsubscript
\usepackage[
  backend=biber,
%  style=alphabetic,
%  citestyle=numeric
]{biblatex}
\bibliography{paper.bib}

% --- Splitting \texttt --------------------------------------------------

\let\textttOrig=\texttt
\def\texttt#1{\expandafter\textttOrig{\seqsplit{#1}}}
\renewcommand{\seqinsert}{\ifmmode
  \allowbreak
  \else\penalty6000\hspace{0pt plus 0.02em}\fi}

% --- Pandoc does not distinguish between links like [foo](bar) and
% --- [foo](foo) -- a simplistic Markdown model.  However, this is
% --- wrong:  in links like [foo](foo) the text is the url, and must
% --- be split correspondingly.
% --- Here we detect links \href{foo}{foo}, and also links starting
% --- with https://doi.org, and use path-like splitting (but not
% --- escaping!) with these links.
% --- Another vile thing pandoc does is the different escaping of
% --- foo and bar.  This may confound our detection.
% --- This problem we do not try to solve at present, with the exception
% --- of doi-like urls, which we detect correctly.

\makeatletter
\let\href@Orig=\href
\def\href@Urllike#1#2{\href@Orig{#1}{\begingroup
    \def\Url@String{#2}\Url@FormatString
    \endgroup}}
\def\href@Notdoi#1#2{\def\tempa{#1}\def\tempb{#2}%
  \ifx\tempa\tempb\relax\href@Urllike{#1}{#2}\else
  \href@Orig{#1}{#2}\fi}
\def\href#1#2{%
  \IfBeginWith{#1}{https://doi.org}%
  {\href@Urllike{#1}{#2}}{\href@Notdoi{#1}{#2}}}
\makeatother

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

% --- Page layout -------------------------------------------------------------
\usepackage[top=3.5cm, bottom=3cm, right=1.5cm, left=1.0cm,
            headheight=2.2cm, reversemp, includemp, marginparwidth=4.5cm]{geometry}

% --- Default font ------------------------------------------------------------
\renewcommand\familydefault{\sfdefault}

% --- Style -------------------------------------------------------------------
\renewcommand{\bibfont}{\small \sffamily}
\renewcommand{\captionfont}{\small\sffamily}
\renewcommand{\captionlabelfont}{\bfseries}

% --- Section/SubSection/SubSubSection ----------------------------------------
\titleformat{\section}
  {\normalfont\sffamily\Large\bfseries}
  {}{0pt}{}
\titleformat{\subsection}
  {\normalfont\sffamily\large\bfseries}
  {}{0pt}{}
\titleformat{\subsubsection}
  {\normalfont\sffamily\bfseries}
  {}{0pt}{}
\titleformat*{\paragraph}
  {\sffamily\normalsize}

% --- Header / Footer ---------------------------------------------------------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
%\renewcommand{\headrulewidth}{0.50pt}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[L]{\hspace{-0.75cm}\includegraphics[width=5.5cm]{logo.png}}
\fancyhead[C]{}
\fancyhead[R]{}
\renewcommand{\footrulewidth}{0.25pt}

\fancyfoot[L]{\parbox[t]{0.98\headwidth}{\footnotesize{\sffamily Hemantakumar Phurailatpam , Anupreeta More, Harsh Narola, Ng Chung Yin (Leo), Justin Janquart, Chris Van Den Broeck, Otto Akseli Hannuksela, Neha Singh, and David Keitel, (2024). \texttt{gwsnr}:
A Python Package for Efficient SNR Calculation of Gravitational
Waves. \textit{PendingJournal of Open Source Software}, Pending(Pending), Pending. \url{https://doi.org/10.xxxxxx/draft}}}}

\fancyfoot[R]{\sffamily \thepage}
\makeatletter
\let\ps@plain\ps@fancy
\fancyheadoffset[L]{4.5cm}
\fancyfootoffset[L]{4.5cm}

% --- Macros ---------

\definecolor{linky}{rgb}{0.0, 0.5, 1.0}

\newtcolorbox{repobox}
   {colback=red, colframe=red!75!black,
     boxrule=0.5pt, arc=2pt, left=6pt, right=6pt, top=3pt, bottom=3pt}

\newcommand{\ExternalLink}{%
   \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{%
       \begin{scope}[x=1ex, y=1ex]
           \clip (-0.1,-0.1)
               --++ (-0, 1.2)
               --++ (0.6, 0)
               --++ (0, -0.6)
               --++ (0.6, 0)
               --++ (0, -1);
           \path[draw,
               line width = 0.5,
               rounded corners=0.5]
               (0,0) rectangle (1,1);
       \end{scope}
       \path[draw, line width = 0.5] (0.5, 0.5)
           -- (1, 1);
       \path[draw, line width = 0.5] (0.6, 1)
           -- (1, 1) -- (1, 0.6);
       }
   }

% --- Title / Authors ---------------------------------------------------------
% patch \maketitle so that it doesn't center
\patchcmd{\@maketitle}{center}{flushleft}{}{}
\patchcmd{\@maketitle}{center}{flushleft}{}{}
% patch \maketitle so that the font size for the title is normal
\patchcmd{\@maketitle}{\LARGE}{\LARGE\sffamily}{}{}
% patch the patch by authblk so that the author block is flush left
\def\maketitle{{%
  \renewenvironment{tabular}[2][]
    {\begin{flushleft}}
    {\end{flushleft}}
  \AB@maketitle}}
\makeatletter
\renewcommand\AB@affilsepx{ \protect\Affilfont}
%\renewcommand\AB@affilnote[1]{{\bfseries #1}\hspace{2pt}}
\renewcommand\AB@affilnote[1]{{\bfseries #1}\hspace{3pt}}
\renewcommand{\affil}[2][]%
   {\newaffiltrue\let\AB@blk@and\AB@pand
      \if\relax#1\relax\def\AB@note{\AB@thenote}\else\def\AB@note{#1}%
        \setcounter{Maxaffil}{0}\fi
        \begingroup
        \let\href=\href@Orig
        \let\texttt=\textttOrig
        \let\protect\@unexpandable@protect
        \def\thanks{\protect\thanks}\def\footnote{\protect\footnote}%
        \@temptokena=\expandafter{\AB@authors}%
        {\def\\{\protect\\\protect\Affilfont}\xdef\AB@temp{#2}}%
         \xdef\AB@authors{\the\@temptokena\AB@las\AB@au@str
         \protect\\[\affilsep]\protect\Affilfont\AB@temp}%
         \gdef\AB@las{}\gdef\AB@au@str{}%
        {\def\\{, \ignorespaces}\xdef\AB@temp{#2}}%
        \@temptokena=\expandafter{\AB@affillist}%
        \xdef\AB@affillist{\the\@temptokena \AB@affilsep
          \AB@affilnote{\AB@note}\protect\Affilfont\AB@temp}%
      \endgroup
       \let\AB@affilsep\AB@affilsepx
}
\makeatother
\renewcommand\Authfont{\sffamily\bfseries}
\renewcommand\Affilfont{\sffamily\small\mdseries}
\setlength{\affilsep}{1em}

\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}

\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{fontspec}

  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}

\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}

\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={gwsnr: A Python Package for Efficient SNR Calculation of Gravitational Waves},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

% --- We redefined \texttt, but in sections and captions we want the
% --- old definition
\let\addcontentslineOrig=\addcontentsline
\def\addcontentsline#1#2#3{\bgroup
  \let\texttt=\textttOrig\addcontentslineOrig{#1}{#2}{#3}\egroup}
\let\markbothOrig\markboth
\def\markboth#1#2{\bgroup
  \let\texttt=\textttOrig\markbothOrig{#1}{#2}\egroup}
\let\markrightOrig\markright
\def\markright#1{\bgroup
  \let\texttt=\textttOrig\markrightOrig{#1}\egroup}

\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\title{\texttt{gwsnr}: A Python Package for Efficient SNR Calculation of
Gravitational Waves}

        \author[1]{Phurailatpam Hemantakumar}
          \author[1]{Otto Akseli HANNUKSELA}

      \affil[1]{Department of Physics, The Chinese University of Hong
Kong, Shatin, New Territories, Hong Kong}
  \date{\vspace{-7ex}}

\begin{document}
\maketitle

\marginpar{

  \begin{flushleft}
  %\hrule
  \sffamily\small

  {\bfseries DOI:} \href{https://doi.org/10.xxxxxx/draft}{\color{linky}{10.xxxxxx/draft}}

  \vspace{2mm}

  {\bfseries Software}
  \begin{itemize}
    \setlength\itemsep{0em}
    \item \href{}{\color{linky}{Review}} \ExternalLink
    \item \href{https://github.com/hemantaph/ler}{\color{linky}{Repository}} \ExternalLink
    \item \href{https://zenodo.org/badge/latestdoi/626733473}{\color{linky}{Archive}} \ExternalLink
  \end{itemize}

  \vspace{2mm}

  \par\noindent\hrulefill\par

  \vspace{2mm}

  {\bfseries Editor:} \href{}{Pending Editor} \ExternalLink \\
  \vspace{1mm}
    {\bfseries Reviewers:}
  \begin{itemize}
  \setlength\itemsep{0em}
    \item \href{https://github.com/Pending Reviewer}{@Pending Reviewer}
    \item \href{https://github.com/}{@}
    \end{itemize}
    \vspace{2mm}

  {\bfseries Submitted:} 3rd July 2024\\
  {\bfseries Published:} 3rd July 2024

  \vspace{2mm}
  {\bfseries License}\\
  Authors of papers retain copyright and release the work under a Creative Commons Attribution 4.0 International License (\href{http://creativecommons.org/licenses/by/4.0/}{\color{linky}{CC BY 4.0}}).

  \end{flushleft}
}

\section{Summary}\label{summary}

Gravitational waves, ripples in spacetime predicted by Einstein's theory
of General Relativity, have revolutionized astrophysics since their
first detection in 2015 (Abbott, B. P. et al. (2016a)). These waves are
emitted by cataclysmic events like the merging of binary black holes
(BBHs), binary neutron stars (BNSs) and BH-NS pairs, providing a unique
window into the cosmos. A critical aspect of gravitational wave analysis
is the Signal-to-Noise Ratio (SNR). SNR quantifies the strength of a
gravitational wave signal relative to the background noise in a
detector, like LIGO (The LIGO Scientific Collaboration et al. (2015)) or
Virgo (Acernese et al. (2014)). This ratio is pivotal in confirming the
detection of gravitational waves and extracting astrophysical
information from them (Abbott, B. P. et al. (2016b)). However, specific
scenarios in gravitational wave research, particularly in simulations of
detectable gravitational wave events (Abbott et al. (2016)) and in
hierarchical Bayesian analysis (Thrane and Talbot (2019)) where
selection effects are considered, demand extensive and efficient
computation of SNR. This requirement presents a significant challenge,
as conventional computational approaches are typically time-consuming
and impractical for such specialized and large-scale analyses (Taylor
and Gerosa (2018), Davide, Pratten, and Vecchio (2020)).

\section{Statement of Need}\label{statement-of-need}

The \emph{\texttt{gwsnr}} Python package addresses the need for
efficient SNR computation in gravitational wave research. It
innovatively streamlines SNR calculations, enhancing accuracy and
efficiency with several advanced techniques. Firstly, it utilizes an
innovative interpolation method, employing a partial-scaling approach
for accurately interpolating the SNR of gravitational waves from
spin-less binary systems wrt to their mass parameters. Secondly, the
package features a noise-weighted inner product method, similar to that
in the \emph{\texttt{bilby}} package (Ashton, Gregory and Biscoveanu,
Sylvia and Cornish, Neil and Dal Canto, Isaac and Kumar, Prayush and
Meacher, Duncan and Middleton, Hannah and Mistry, Divyansh and Smith,
Rory and Stevenson, Tom (2022)), but enhanced with multiprocessing
capabilities. This integration allows for the parallel processing of
complex calculations, thereby expediting the SNR computation. Thirdly, a
trained Artificial Neural Network (ANN) model is incorporated for rapid
`probability of detection' (Pdet) estimation for BBH systems with spin
precession. Lastly, \emph{\texttt{gwsnr}} leverages the
\emph{\texttt{numba}}'s Just-In-Time (njit) compiler (Lam, Pitrou, and
Seibert (2022)), which optimizes performance by compiling Python code
into machine code at runtime, drastically reducing execution times.
Beyond these technical merits, \emph{\texttt{gwsnr}} stands out for its
user-friendly features and seamless integration with other related
software packages, making it not just a powerful tool but also an
accessible one for researchers. These attributes position
\emph{\texttt{gwsnr}} as an invaluable asset in gravitational wave data
analysis, particularly in simulations of detectable binary mergers,
calculation of merger rates, determining gravitational wave lensing
rates ((\textbf{ler?}), Ng et al. (2024)), and in the analysis of
selection effects within hierarchical Bayesian frameworks. The package
thus represents a significant step forward in gravitational wave
research, enabling more precise and efficient exploration of the
universe through gravitational wave observations and simulations.
Additionally, \emph{\texttt{gwsnr}} is instrumental in the
\emph{\texttt{ler}} ((\textbf{ler?})) package for calculating detectable
rates of both lensed and unlensed gravitational wave events, showcasing
its utility in advanced gravitational wave studies.

\section{Mathematical Formulation}\label{mathematical-formulation}

\paragraph{Modified FINDCHIRP Method: Partial Scaling
Approach}\label{modified-findchirp-method-partial-scaling-approach}

The \emph{\texttt{gwsnr}} package introduces the Partial Scaling method
for SNR calculations in spin-less binary systems. This method, rooted in
the FINDCHIRP algorithm (Allen et al. (2012)), focuses on non-spinning
IMR waveforms and particularly interpolates the Partial scaled SNR
(\(\rho_{1/2}\)) based on mass parameters (\(M_{tot},q\)).

\begin{itemize}
\item
  \textbf{Interpolation Method}: Utilizes a 2D cubic spline technique
  (njit-ted) for the `partialsnr' segment.
\item
  \textbf{Equations}:

  \begin{itemize}
  \item
    For a simple inspiral waveform, the optimal SNR is given by,
    \[\rho = F(D_l,\mathcal{M},\iota,\psi,\alpha, \delta, \psi) \sqrt{ 4\int_0^{f_{ISCO}} \frac{f^{-7/3}}{S_n(f)}df }\]
  \item
    \(F\) is defined as a function of luminosity distance (\(D_l\)),
    chirp mass (\(\mathcal{M}\)), inclination angle (\(\iota\)),
    polarization angles (\(\psi\)), right ascension (\(\alpha\)), and
    declination (\(\delta\)). \(f\) is the frequency, \(f_{ISCO}\) is
    the last stable orbit frequency and \(S_n(f)\) is the detector's
    noise curve or power spectral density (psd).
  \item
    Then, partial scaled SNR:
    \(\rho_{1/2} = \sqrt{ 4\int_0^\infty \frac{f^{-7/3}}{S_n(f)}df } \approx \sqrt{ 4\int_0^{f_{ISCO}} \frac{f^{-7/3}}{S_n(f)}df }\)
  \item
    For an spinless frequency-domain IMR (Inspiral-Merger-Ringdown)
    waveform with optimal SNR equal to \(\rho\):
    \(\rho_{1/2} = \rho\,/\, F(D_l,\mathcal{M},\iota,\psi,\alpha, \delta, \psi)\)
  \item
    \(\rho_{1/2}\) is considered a function of \(M_{tot}\) and \(q\).
  \end{itemize}
\end{itemize}

\paragraph{Noise-Weighted Inner Product
Method}\label{noise-weighted-inner-product-method}

Designed for SNR calculations in systems characterized by frequency
domain waveforms in \emph{\texttt{lalsimulation}} (LIGO Scientific
Collaboration, Virgo Collaboration, and KAGRA Collaboration (2018)),
including spin-precessing binary systems.

\begin{itemize}
\item
  \textbf{Methodology}: Combines waveform generation (multi-process),
  antenna pattern calculation (njit-ted), and noise-weighted inner
  product computation (njit-ted).
\item
  \textbf{Equations}:

  \begin{itemize}
  \item
    Inner product:
    \(\left< a | b \right> = 4 \int_{f_{min}}^{f_{max}} \frac{\tilde{a}(f)\tilde{b}^*(f)}{S_n(f)} df\)
  \item
    Optimal SNR:
    \(\rho = \sqrt{ F_+^2 \left< \tilde{h}_+ | \tilde{h}_+ \right> + F_{\times}^2 \left< \tilde{h}_{\times} | \tilde{h}_{\times} \right> }\),
    for orthogonal \(h_+\) and \(h_{\times}\).
  \item
    \(h_{+\times}\) are frequency domain waveform polarizations, and
    \(F_{+\times}\) are antenna patterns.
  \end{itemize}
\end{itemize}

These formulations highlight \emph{\texttt{gwsnr}}'s capability to
efficiently process diverse gravitational wave signals, enhancing data
analysis accuracy and efficiency.

\paragraph{Artificial Neural Network (ANN) Model for Pdet
Estimation}\label{artificial-neural-network-ann-model-for-pdet-estimation}

The \emph{\texttt{gwsnr}} package now incorporates an artificial neural
network (ANN) model, developed using \emph{\texttt{TensorFlow}} (Abadi
et al. (2015)) and \emph{\texttt{sklearn}} (Pedregosa et al. (2011)), to
rapidly estimate the `probability of detection' (Pdet) in binary black
hole (BBH) systems using the IMRPhenomXPHM waveform approximant. This
complex inspiral-merger-ringdown (IMR) waveform model accounts for
spin-precessing systems with subdominant harmonics. The ANN model is
especially useful when precise signal-to-noise ratio (SNR) calculations
are not critical, providing a quick and effective means of estimating
Pdet. This value indicates detectability under Gaussian noise by
determining if the SNR exceeds a certain threshold. Trained on a large
dataset from the \emph{\texttt{ler}} package, the ANN model uses
`partial scaled SNR' values as a primary input, reducing input
dimensionality from 15 to 5 and enhancing accuracy. This approach offers
a practical solution for assessing detectability under specified
conditions.

\section{Acknowledgements}\label{acknowledgements}

The author gratefully acknowledges the substantial contributions from
all who supported this research. Special thanks go to my academic
advisors for their invaluable guidance and unwavering support. The
interactions with my research colleagues have greatly enriched this
work. The Department of Physics at The Chinese University of Hong Kong
is acknowledged for the Postgraduate Studentship that made this research
possible. Thanks are also due to the LIGO Laboratory for the
computational resources, supported by National Science Foundation Grants
No.~PHY-0757058 and No.~PHY-0823459.

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-tensorflow2015}
Abadi, Martín, Ashish Agarwal, Paul Barham, Eugene Brevdo, Zhifeng Chen,
Craig Citro, Greg S. Corrado, et al. 2015. {``{TensorFlow}: Large-Scale
Machine Learning on Heterogeneous Systems.''}
\url{https://www.tensorflow.org/}.

\bibitem[\citeproctext]{ref-Abbott:2016:rates}
Abbott, B. P., R. Abbott, T. D. Abbott, M. R. Abernathy, F. Acernese, K.
Ackley, C. Adams, et al. 2016. {``ASTROPHYSICAL IMPLICATIONS OF THE
BINARY BLACK HOLE MERGER GW150914.''} \emph{The Astrophysical Journal
Letters} 818 (2): L22.
\url{https://doi.org/10.3847/2041-8205/818/2/l22}.

\bibitem[\citeproctext]{ref-Abbott:2016}
Abbott, B. P., R. Abbott, T. D. Abbott, M. R. Abernathy, F. Acernese, K.
Ackley, C. Adams, et al. 2016a. {``Observation of Gravitational Waves
from a Binary Black Hole Merger.''} \emph{Physical Review Letters} 116
(6). \url{https://doi.org/10.1103/physrevlett.116.061102}.

\bibitem[\citeproctext]{ref-Abbott:2016:detection}
Abbott, B. P., R. Abbott, T. D. Abbott, M. R. Abernathy, F. Acernese, K.
Ackley, C. Adams, et al. 2016b. {``GW150914: First Results from the
Search for Binary Black Hole Coalescence with Advanced LIGO.''}
\emph{Physical Review D} 93 (12).
\url{https://doi.org/10.1103/physrevd.93.122003}.

\bibitem[\citeproctext]{ref-VIRGO2015}
Acernese, F, M Agathos, K Agatsuma, D Aisa, N Allemandou, A Allocca, J
Amarni, et al. 2014. {``Advanced Virgo: A Second-Generation
Interferometric Gravitational Wave Detector.''} \emph{Classical and
Quantum Gravity} 32 (2): 024001.
\url{https://doi.org/10.1088/0264-9381/32/2/024001}.

\bibitem[\citeproctext]{ref-Allen:2012}
Allen, Bruce, Warren G. Anderson, Patrick R. Brady, Duncan A. Brown, and
Jolien D. E. Creighton. 2012. {``FINDCHIRP: An Algorithm for Detection
of Gravitational Waves from Inspiraling Compact Binaries.''}
\emph{Physical Review D} 85 (12).
\url{https://doi.org/10.1103/physrevd.85.122006}.

\bibitem[\citeproctext]{ref-bilby}
Ashton, Gregory and Biscoveanu, Sylvia and Cornish, Neil and Dal Canto,
Isaac and Kumar, Prayush and Meacher, Duncan and Middleton, Hannah and
Mistry, Divyansh and Smith, Rory and Stevenson, Tom. 2022. {``{bilby: a
user-friendly Bayesian inference library}.''} \emph{GitHub Repository}.
GitHub. \url{https://github.com/GregoryAshton/Bilby}.

\bibitem[\citeproctext]{ref-Gerosa:2020}
Davide, Gerosa, Geraint Pratten, and Alberto Vecchio. 2020.
{``Gravitational-Wave Selection Effects Using Neural-Network
Classifiers.''} \emph{Physical Review D} 102 (10).
\url{https://doi.org/10.1103/physrevd.102.103020}.

\bibitem[\citeproctext]{ref-numba}
Lam, Stan, Stéphane Pitrou, and Mark Seibert. 2022. {``Numba: A High
Performance Python Compiler.''} \emph{Numba Documentation}. Anaconda,
Inc. \url{https://numba.pydata.org/}.

\bibitem[\citeproctext]{ref-lalsuite}
LIGO Scientific Collaboration, Virgo Collaboration, and KAGRA
Collaboration. 2018. {``{LVK} {A}lgorithm {L}ibrary - {LALS}uite.''}
Free software (GPL). \url{https://doi.org/10.7935/GT1W-FZ16}.

\bibitem[\citeproctext]{ref-ng2024}
Ng, Leo C. Y., Justin Janquart, Hemantakumar Phurailatpam, Harsh Narola,
Jason S. C. Poon, Chris Van Den Broeck, and Otto A. Hannuksela. 2024.
{``Uncovering Faint Lensed Gravitational-Wave Signals and Reprioritizing
Their Follow-up Analysis Using Galaxy Lensing Forecasts with Detected
Counterparts.''} \url{https://arxiv.org/abs/2403.16532}.

\bibitem[\citeproctext]{ref-scikitlearn}
Pedregosa, Fabian, Gaël Varoquaux, Alexandre Gramfort, Vincent Michel,
Bertrand Thirion, Olivier Grisel, Mathieu Blondel, et al. 2011.
{``Scikit-Learn: Machine Learning in {P}ython.''} \emph{Journal of
Machine Learning Research} 12: 2825--30.

\bibitem[\citeproctext]{ref-Taylor:2018}
Taylor, Stephen R., and Davide Gerosa. 2018. {``Mining
Gravitational-Wave Catalogs to Understand Binary Stellar Evolution: A
New Hierarchical Bayesian Framework.''} \emph{Physical Review D} 98 (8).
\url{https://doi.org/10.1103/physrevd.98.083017}.

\bibitem[\citeproctext]{ref-LIGO2015}
The LIGO Scientific Collaboration, J Aasi, B P Abbott, R Abbott, T
Abbott, M R Abernathy, K Ackley, et al. 2015. {``Advanced LIGO.''}
\emph{Classical and Quantum Gravity} 32 (7): 074001.
\url{https://doi.org/10.1088/0264-9381/32/7/074001}.

\bibitem[\citeproctext]{ref-Thrane:2019}
Thrane, Eric, and Colm Talbot. 2019. {``An Introduction to Bayesian
Inference in Gravitational-Wave Astronomy: Parameter Estimation, Model
Selection, and Hierarchical Models.''} \emph{Publications of the
Astronomical Society of Australia} 36.
\url{https://doi.org/10.1017/pasa.2019.2}.

\end{CSLReferences}

\end{document}

### 2024-11-05 gwsnr/gwsnr.py

@@ -1547,7 +1547,7 @@ class GWSNR:
 
         dl_eff = np.sqrt(np.sum(dl_eff**2))
         horizon["net"] = (dl_eff / snr_th_net) * optimal_snr_unscaled["optimal_snr_net"]
-        print('dl_eff', dl_eff)
-        print('optimal_snr_unscaled', optimal_snr_unscaled["optimal_snr_net"])
+        #print('dl_eff', dl_eff)
+        #print('optimal_snr_unscaled', optimal_snr_unscaled["optimal_snr_net"])
 
         return horizon

### 2024-11-05 arxiv/paper.tex
mac

@@
 
-\fancyfoot[L]{\parbox[t]{0.98\headwidth}{\footnotesize{\sffamily Hemantakumar Phurailatpam , Anupreeta More, Harsh Narola, Ng Chung Yin (Leo), Justin Janquart, Chris Van Den Broeck, Otto Akseli Hannuksela, Neha Singh, and David Keitel, (2024).
-\texttt{gwsnr}:
+\fancyfoot[L]{\parbox[t]{0.98\headwidth}{\footnotesize{\sffamily Hemantakumar Phurailatpam, Otto Akseli Hannuksela, (2024). \texttt{gwsnr}:
 A Python Package for Efficient SNR Calculation of Gravitational
@@
 calculation of merger rates, determining gravitational wave lensing
-rates ((\textbf{ler?}), Ng et al. (2024)), and in the analysis of
-selection effects within hierarchical Bayesian frameworks. The package
-thus represents a significant step forward in gravitational wave
-research, enabling more precise and efficient exploration of the
+rates (Phurailatpam et al. (2024), Ng et al. (2024)), and in the
+analysis of selection effects within hierarchical Bayesian frameworks.
+The package thus represents a significant step forward in gravitational
+wave research, enabling more precise and efficient exploration of the
 universe through gravitational wave observations and simulations.
 Additionally, \emph{\texttt{gwsnr}} is instrumental in the
-\emph{\texttt{ler}} ((\textbf{ler?})) package for calculating detectable
-rates of both lensed and unlensed gravitational wave events, showcasing
-its utility in advanced gravitational wave studies.
+\emph{\texttt{ler}} (Phurailatpam et al. (2024)) package for calculating
+detectable rates of both lensed and unlensed gravitational wave events,
+showcasing its utility in advanced gravitational wave studies.
 
@@
 
+\bibitem[\citeproctext]{ref-ler}
+Phurailatpam, Hemantakumar, Anupreeta More, Harsh Narola, Ng Chung Yin,
+Justin Janquart, Chris Van Den Broeck, Otto Akseli Hannuksela, Neha
+Singh, and David Keitel. 2024. {``Ler : LVK (LIGO-Virgo-KAGRA
+Collaboration) Event (Compact-Binary Mergers) Rate Calculator and
+Simulator.''} \url{https://arxiv.org/abs/2407.07526}.
+
 \bibitem[\citeproctext]{ref-Taylor:2018}

### 2024-11-05 arxiv/paper.tex
mac

@@
 \fancyfoot[L]{\parbox[t]{0.98\headwidth}{\footnotesize{\sffamily Hemantakumar Phurailatpam, Otto Akseli Hannuksela, (2024). \texttt{gwsnr}:
-A Python Package for Efficient SNR Calculation of Gravitational
-Waves. \textit{PendingJournal of Open Source Software}, Pending(Pending), Pending. \url{https://doi.org/10.xxxxxx/draft}}}}
+A Python Package for Efficient SNR Calculation of
+GWs. \textit{PendingJournal of Open Source Software}, Pending(Pending), Pending. \url{https://doi.org/10.xxxxxx/draft}}}}
 
@@
 \hypersetup{unicode=true,
-            pdftitle={gwsnr: A Python Package for Efficient SNR Calculation of Gravitational Waves},
+            pdftitle={gwsnr: A Python Package for Efficient SNR Calculation of GWs},
             pdfborder={0 0 0},
@@
 \title{\texttt{gwsnr}: A Python Package for Efficient SNR Calculation of
-Gravitational Waves}
+GWs}
 
@@
 
-Gravitational waves, ripples in spacetime predicted by Einstein's theory
-of General Relativity, have revolutionized astrophysics since their
-first detection in 2015 (Abbott, B. P. et al. (2016a)). These waves are
-emitted by cataclysmic events like the merging of binary black holes
-(BBHs), binary neutron stars (BNSs) and BH-NS pairs, providing a unique
-window into the cosmos. A critical aspect of gravitational wave analysis
-is the Signal-to-Noise Ratio (SNR). SNR quantifies the strength of a
-gravitational wave signal relative to the background noise in a
-detector, like LIGO (The LIGO Scientific Collaboration et al. (2015)) or
-Virgo (Acernese et al. (2014)). This ratio is pivotal in confirming the
-detection of gravitational waves and extracting astrophysical
-information from them (Abbott, B. P. et al. (2016b)). However, specific
-scenarios in gravitational wave research, particularly in simulations of
-detectable gravitational wave events (Abbott et al. (2016)) and in
+Gravitational waves (GWs), ripples in spacetime predicted by Einstein's
+theory of General Relativity, have revolutionized astrophysics since
+their first detection in 2015 (Abbott, B. P. et al. (2016a)). These
+waves are emitted by cataclysmic events like the merging of binary black
+holes (BBHs), binary neutron stars (BNSs) and BH-NS pairs, providing a
+unique window into the cosmos. A critical aspect of GW analysis is the
+Signal-to-Noise Ratio (SNR). SNR quantifies the strength of a GW signal
+relative to the background noise in a detector, like LIGO (The LIGO
+Scientific Collaboration et al. (2015)) or Virgo (Acernese et al.
+(2014)). This ratio is pivotal in confirming the detection of GWs and
+extracting astrophysical information from them (Abbott, B. P. et al.
+(2016b)). However, specific scenarios in GW research, particularly in
+simulations of detectable GW events (Abbott et al. (2016)) and in
 hierarchical Bayesian analysis (Thrane and Talbot (2019)) where
@@
 computation of SNR. This requirement presents a significant challenge,
-as conventional computational approaches are typically time-consuming
-and impractical for such specialized and large-scale analyses (Taylor
-and Gerosa (2018), Davide, Pratten, and Vecchio (2020)).
+as conventional computational approaches, such as noise-weighted inner
+product, are typically time-consuming and impractical for such
+specialized and large-scale analyses (Taylor and Gerosa (2018), Davide,
+Pratten, and Vecchio (2020)).
 
@@
 The \emph{\texttt{gwsnr}} Python package addresses the need for
-efficient SNR computation in gravitational wave research. It
-innovatively streamlines SNR calculations, enhancing accuracy and
-efficiency with several advanced techniques. Firstly, it utilizes an
-innovative interpolation method, employing a partial-scaling approach
-for accurately interpolating the SNR of gravitational waves from
-spin-less binary systems wrt to their mass parameters. Secondly, the
-package features a noise-weighted inner product method, similar to that
-in the \emph{\texttt{bilby}} package (Ashton, Gregory and Biscoveanu,
-Sylvia and Cornish, Neil and Dal Canto, Isaac and Kumar, Prayush and
-Meacher, Duncan and Middleton, Hannah and Mistry, Divyansh and Smith,
-Rory and Stevenson, Tom (2022)), but enhanced with multiprocessing
+efficient SNR computation in GW research. It innovatively streamlines
+SNR calculations, enhancing accuracy and efficiency with several
+advanced techniques. Firstly, it utilizes an innovative interpolation
+method, employing a partial-scaling approach for accurately
+interpolating the SNR of GWs from spin-less binary systems wrt to their
+mass parameters. Secondly, the package features a noise-weighted inner
+product method, similar to that in the \emph{\texttt{bilby}} package
+(Ashton, Gregory et al. (2022)), but enhanced with multiprocessing
 capabilities. This integration allows for the parallel processing of
@@
 accessible one for researchers. These attributes position
-\emph{\texttt{gwsnr}} as an invaluable asset in gravitational wave data
-analysis, particularly in simulations of detectable binary mergers,
-calculation of merger rates, determining gravitational wave lensing
-rates (Phurailatpam et al. (2024), Ng et al. (2024)), and in the
-analysis of selection effects within hierarchical Bayesian frameworks.
-The package thus represents a significant step forward in gravitational
-wave research, enabling more precise and efficient exploration of the
-universe through gravitational wave observations and simulations.
+\emph{\texttt{gwsnr}} as an invaluable asset in GW data analysis,
+particularly in simulations of detectable compact binary mergers,
+determining rates of GW events, ascertain to both lensed and un-lensed
+events (Phurailatpam et al. (2024), Ng et al. (2024)), and in the
+analysis of selection effects within hierarchical Bayesian frameworks
+(Thrane and Talbot (2019)). The package thus represents a significant
+step forward in aiding GW research, enabling more precise and efficient
+exploration of the universe through GW observations and simulations.
 Additionally, \emph{\texttt{gwsnr}} is instrumental in the
 \emph{\texttt{ler}} (Phurailatpam et al. (2024)) package for calculating
-detectable rates of both lensed and unlensed gravitational wave events,
-showcasing its utility in advanced gravitational wave studies.
+detectable rates of both lensed and unlensed GW events, showcasing its
+utility in advanced GW studies.
 
@@
 the FINDCHIRP algorithm (Allen et al. (2012)), focuses on non-spinning
-IMR waveforms and particularly interpolates the Partial scaled SNR
+inspiral-merger-ringdown (IMR) waveforms, in lalsimulation library (LIGO
+Scientific Collaboration, Virgo Collaboration, and KAGRA Collaboration
+(2018)), and particularly interpolates the Partial scaled SNR
 (\(\rho_{1/2}\)) based on mass parameters (\(M_{tot},q\)).
@@
     For a simple inspiral waveform, the optimal SNR is given by,
-    \[\rho = F(D_l,\mathcal{M},\iota,\psi,\alpha, \delta, \psi) \sqrt{ 4\int_0^{f_{ISCO}} \frac{f^{-7/3}}{S_n(f)}df }\]
+    \[\rho = F(D_l,\mathcal{M},\iota,\psi,\alpha, \delta) \sqrt{ 4\int_0^{f_{ISCO}} \frac{f^{-7/3}}{S_n(f)}df }\]
   \item
@@
   \item
-    For an spinless frequency-domain IMR (Inspiral-Merger-Ringdown)
-    waveform with optimal SNR equal to \(\rho\):
+    For an spinless frequency-domain IMR waveform with optimal SNR equal
+    to \(\rho\):
     \(\rho_{1/2} = \rho\,/\, F(D_l,\mathcal{M},\iota,\psi,\alpha, \delta, \psi)\)
@@
 
-\paragraph{Noise-Weighted Inner Product
-Method}\label{noise-weighted-inner-product-method}
+\paragraph{Noise-Weighted Inner Product Method with
+Multiprocessing}\label{noise-weighted-inner-product-method-with-multiprocessing}
 
@@
 These formulations highlight \emph{\texttt{gwsnr}}'s capability to
-efficiently process diverse gravitational wave signals, enhancing data
-analysis accuracy and efficiency.
+efficiently process diverse GW signals, enhancing data analysis accuracy
+and efficiency.
 
@@
 et al. (2015)) and \emph{\texttt{sklearn}} (Pedregosa et al. (2011)), to
-rapidly estimate the `probability of detection' (Pdet) in binary black
-hole (BBH) systems using the IMRPhenomXPHM waveform approximant. This
-complex inspiral-merger-ringdown (IMR) waveform model accounts for
-spin-precessing systems with subdominant harmonics. The ANN model is
-especially useful when precise signal-to-noise ratio (SNR) calculations
-are not critical, providing a quick and effective means of estimating
-Pdet. This value indicates detectability under Gaussian noise by
-determining if the SNR exceeds a certain threshold. Trained on a large
-dataset from the \emph{\texttt{ler}} package, the ANN model uses
+rapidly estimate the Pdet in binary black hole (BBH) systems using the
+IMRPhenomXPHM waveform approximant. This complex IMR waveform model
+accounts for spin-precessing systems with subdominant harmonics. The ANN
+model is especially useful when precise signal-to-noise ratio (SNR)
+calculations are not critical, providing a quick and effective means of
+estimating Pdet. This value indicates detectability under Gaussian noise
+by determining if the SNR exceeds a certain threshold. Trained on a
+large dataset from the \emph{\texttt{ler}} package, the ANN model uses
 `partial scaled SNR' values as a primary input, reducing input
@@
 \bibitem[\citeproctext]{ref-bilby}
-Ashton, Gregory and Biscoveanu, Sylvia and Cornish, Neil and Dal Canto,
-Isaac and Kumar, Prayush and Meacher, Duncan and Middleton, Hannah and
-Mistry, Divyansh and Smith, Rory and Stevenson, Tom. 2022. {``{bilby: a
-user-friendly Bayesian inference library}.''} \emph{GitHub Repository}.
-GitHub. \url{https://github.com/GregoryAshton/Bilby}.
+Ashton, Gregory, Sylvia Biscoveanu, Neil Cornish, Isaac Dal Canto,
+Prayush Kumar, Duncan Meacher, Hannah Middleton, Divyansh Mistry, Rory
+Smith, and Tom Stevenson. 2022. {``{bilby: a user-friendly Bayesian
+inference library}.''} \emph{GitHub Repository}. GitHub.
+\url{https://github.com/GregoryAshton/Bilby}.
 

### 2024-11-07 arxiv/paper.tex
mac

@@
 product, are typically time-consuming and impractical for such
-specialized and large-scale analyses (Taylor and Gerosa (2018), Davide,
-Pratten, and Vecchio (2020)).
+specialized and large-scale analyses (Taylor and Gerosa (2018), Gerosa
+et al. (2020)).
 
@@
 a practical solution for assessing detectability under specified
-conditions.
+conditions. Other similar efforts with ANN models are detailed in
+Chapman-Bird et al. (2023), Gerosa et al. (2020) etc.
 
@@
 
+\bibitem[\citeproctext]{ref-ChapmanBird2023}
+Chapman-Bird, Christian E A et al. 2023. {``Rapid Determination of LISA
+Sensitivity to Extreme Mass Ratio Inspirals with Machine Learning.''}
+\emph{Monthly Notices of the Royal Astronomical Society} 522 (4):
+6043--54. \url{https://doi.org/10.1093/mnras/stad1397}.
+
 \bibitem[\citeproctext]{ref-Gerosa:2020}
-Davide, Gerosa, Geraint Pratten, and Alberto Vecchio. 2020.
-{``Gravitational-Wave Selection Effects Using Neural-Network
-Classifiers.''} \emph{Physical Review D} 102 (10).
+Gerosa, Davide et al. 2020. {``Gravitational-Wave Selection Effects
+Using Neural-Network Classifiers.''} \emph{Physical Review D} 102 (10).
 \url{https://doi.org/10.1103/physrevd.102.103020}.

### 2024-11-09 arxiv/paper.tex
mac

@@
 relative to the background noise in a detector, like LIGO (The LIGO
-Scientific Collaboration et al. (2015)) or Virgo (Acernese et al.
-(2014)). This ratio is pivotal in confirming the detection of GWs and
-extracting astrophysical information from them (Abbott, B. P. et al.
-(2016b)). However, specific scenarios in GW research, particularly in
-simulations of detectable GW events (Abbott et al. (2016)) and in
-hierarchical Bayesian analysis (Thrane and Talbot (2019)) where
-selection effects are considered, demand extensive and efficient
-computation of SNR. This requirement presents a significant challenge,
-as conventional computational approaches, such as noise-weighted inner
-product, are typically time-consuming and impractical for such
-specialized and large-scale analyses (Taylor and Gerosa (2018), Gerosa
-et al. (2020)).
+Scientific Collaboration et al. (2015), Abbott et al. (2020), Buikema et
+al. (2020)), Virgo (F. Acernese et al. (2014), F. Acernese et al.
+(2019)) or KAGRA (Akutsu et al. (2020), Aso et al. (2013)). This ratio
+is pivotal in confirming the detection of GWs and extracting
+astrophysical information from them (Abbott, B. P. et al. (2016b)).
+However, specific scenarios in GW research, particularly in simulations
+of detectable GW events (Abbott et al. (2016)) and in hierarchical
+Bayesian analysis (Thrane and Talbot (2019)) where selection effects are
+considered, demand extensive and efficient computation of SNR. This
+requirement presents a significant challenge, as conventional
+computational approaches, such as noise-weighted inner product, are
+typically time-consuming and impractical for such specialized and
+large-scale analyses (Taylor and Gerosa (2018), Gerosa et al. (2020)).
 
@@
 particularly in simulations of detectable compact binary mergers,
-determining rates of GW events, ascertain to both lensed and un-lensed
+determining rates of GW events, related to both lensed and un-lensed
 events (Phurailatpam et al. (2024), Ng et al. (2024)), and in the
@@
     polarization angles (\(\psi\)), right ascension (\(\alpha\)), and
-    declination (\(\delta\)). \(f\) is the frequency, \(f_{ISCO}\) is
-    the last stable orbit frequency and \(S_n(f)\) is the detector's
-    noise curve or power spectral density (psd).
+    declination (\(\delta\)), refer to Eqn(D1) of Allen et al. (2012).
+    \(f\) is the frequency, \(f_{ISCO}\) is the last stable orbit
+    frequency and \(S_n(f)\) is the detector's noise curve or power
+    spectral density (psd).
   \item
@@
     to \(\rho\):
-    \(\rho_{1/2} = \rho\,/\, F(D_l,\mathcal{M},\iota,\psi,\alpha, \delta, \psi)\)
+    \(\rho_{1/2} = \rho\,/\, F(D_l,\mathcal{M},\iota,\psi,\alpha, \delta)\)
   \item
@@
 
+\bibitem[\citeproctext]{ref-Abbott2020}
+Abbott, B. P., R. Abbott, T. D. Abbott, S. Abraham, F. Acernese, K.
+Ackley, C. Adams, et al. 2020. {``Prospects for Observing and Localizing
+Gravitational-Wave Transients with Advanced LIGO, Advanced Virgo and
+KAGRA.''} \emph{Living Reviews in Relativity} 23 (1).
+\url{https://doi.org/10.1007/s41114-020-00026-9}.
+
+\bibitem[\citeproctext]{ref-virgo:2019}
+Acernese, F., M. Agathos, L. Aiello, A. Allocca, A. Amato, S. Ansoldi,
+S. Antier, et al. 2019. {``Increasing the Astrophysical Reach of the
+Advanced Virgo Detector via the Application of Squeezed Vacuum States of
+Light.''} \emph{Phys. Rev. Lett.} 123 (December): 231108.
+\url{https://doi.org/10.1103/PhysRevLett.123.231108}.
+
 \bibitem[\citeproctext]{ref-VIRGO2015}
@@
 \url{https://doi.org/10.1088/0264-9381/32/2/024001}.
+
+\bibitem[\citeproctext]{ref-akutsu2020overviewkagradetectordesign}
+Akutsu, T., M. Ando, K. Arai, Y. Arai, S. Araki, A. Araya, N. Aritomi,
+et al. 2020. {``Overview of KAGRA: Detector Design and Construction
+History.''} \url{https://arxiv.org/abs/2005.05574}.
 
@@
 \url{https://github.com/GregoryAshton/Bilby}.
+
+\bibitem[\citeproctext]{ref-PhysRevD:88:043007}
+Aso, Yoichi, Yuta Michimura, Kentaro Somiya, Masaki Ando, Osamu
+Miyakawa, Takanori Sekiguchi, Daisuke Tatsumi, and Hiroaki Yamamoto.
+2013. {``Interferometer Design of the KAGRA Gravitational Wave
+Detector.''} \emph{Phys. Rev. D} 88 (August): 043007.
+\url{https://doi.org/10.1103/PhysRevD.88.043007}.
+
+\bibitem[\citeproctext]{ref-PhysRevD.102.062003}
+Buikema, A., C. Cahillane, G. L. Mansell, C. D. Blair, R. Abbott, C.
+Adams, R. X. Adhikari, et al. 2020. {``Sensitivity and Performance of
+the Advanced LIGO Detectors in the Third Observing Run.''} \emph{Phys.
+Rev. D} 102 (September): 062003.
+\url{https://doi.org/10.1103/PhysRevD.102.062003}.
 

### 2024-11-22 gwsnr/__init__.py
mac

@@ -13,29 +13,31 @@ __version__ = "0.3.2"
 import os
 __file__ = os.path.abspath(__file__)
 
-import multiprocessing as mp
+# import multiprocessing as mp
 
-def set_multiprocessing_start_method():
-    if os.name == 'posix':  # posix indicates the program is run on Unix/Linux/MacOS
-      try:
-         mp.set_start_method('fork', force=True)
-      except RuntimeError:
-         # The start method can only be set once and must be set before any process starts
-         pass
-    else:
-      # For Windows and other operating systems, use 'spawn'
-      try:
-         mp.set_start_method('spawn', force=True)
-      except RuntimeError:
-         pass
+# def set_multiprocessing_start_method():
+#     if os.name == 'posix':  # posix indicates the program is run on Unix/Linux/MacOS
+#       try:
+#          mp.set_start_method('fork', force=True)
+#       except RuntimeError:
+#          # The start method can only be set once and must be set before any process starts
+#          pass
+#     else:
+#       # For Windows and other operating systems, use 'spawn'
+#       try:
+#          mp.set_start_method('spawn', force=True)
+#       except RuntimeError:
+#          pass
 
-set_multiprocessing_start_method()
+# set_multiprocessing_start_method()
 
 from .gwsnr import *
 from .njit_functions import *
 from .multiprocessing_routine import *
 # from .pdet import *
 from .utils import *
+from .ripple_class import *
+from .jaxjit_functions import *
 
 from . import ann
 

### 2024-11-22 gwsnr/gwsnr.py

@@ -1,6 +1,6 @@
 # -*- coding: utf-8 -*-
 """
-This module contains functions for calculating the SNR of a CBC signal. It has two methods: interpolation (bicubic) and inner product. Interpolation method is much faster than inner product method. Interpolation method is tested for IMRPhenomD and TaylorF2 waveform approximants for the spinless scenario.
+This module contains functions for calculating the SNR of a CBC signal. It has two methods: interpolation (bicubic) and inner product (multiprocessing and jax.jit+jax.vmap). Interpolation method is much faster than inner product method. Interpolation method is tested for IMRPhenomD and TaylorF2 waveform approximants for the spinless scenario.
 """
 
 import os
@@ -11,6 +11,14 @@ from tqdm import tqdm
 from scipy.stats import norm
 from scipy.interpolate import CubicSpline
 from scipy.optimize import fsolve
+
+# warning suppression lal
+import warnings
+warnings.filterwarnings("ignore", "Wswiglal-redir-stdio")
+import lal
+lal.swig_redirect_standard_output_error(False)
+
+from .ripple_class import RippleInnerProduct
 
 from .utils import (
     dealing_with_psds,
@@ -68,7 +76,7 @@ class GWSNR:
         Minimum frequency of the waveform. Default is 20.0.
     snr_type : `str`
         Type of SNR calculation. Default is 'interpolation'.
-        options: 'interpolation', 'inner_product', 'pdet', 'ann'
+        options: 'interpolation', 'inner_product', 'inner_product_jax', 'pdet', 'ann'
     psds : `dict`
         Dictionary of psds for different detectors. Default is None. If None, bilby's default psds will be used. Other options:\n
         Example 1: when values are psd name from pycbc analytical psds, psds={'L1':'aLIGOaLIGODesignSensitivityT1800044','H1':'aLIGOaLIGODesignSensitivityT1800044','V1':'AdvVirgo'}. To check available psd name run \n
@@ -177,6 +185,11 @@ class GWSNR:
     +-------------------------------------+----------------------------------+
     |:meth:`~compute_bilby_snr`           | Calculates SNR using             |
     |                                     | inner product method.            |
+    |                                     | (python multiprocessing)         |
+    +-------------------------------------+----------------------------------+
+    |:meth:`~compute_ripple_snr`          | Calculates SNR using             |
+    |                                     | inner product method.            |
+    |                                     | (jax.jit+jax.vmap)               |
[…]

### 2024-11-22 gwsnr/jaxjit_functions.py

@@ -1,0 +1,80 @@
+from jax import jit
+import jax.numpy as jnp
+
+@jit
+def findchirp_chirptime_jax(m1, m2, fmin):
+    """
+    Time taken from f_min to f_lso (last stable orbit). 3.5PN in fourier phase considered.
+
+    Parameters
+    ----------
+    m1 : `float`
+        Mass of the first body in solar masses.
+    m2 : `float`
+        Mass of the second body in solar masses.
+    fmin : `float`
+        Lower frequency cutoff.
+
+    Returns
+    -------
+    chirp_time : float
+        Time taken from f_min to f_lso (last stable orbit frequency).
+    """
+
+    Gamma = 0.5772156649015329
+    Pi = jnp.pi
+    MTSUN_SI = 4.925491025543576e-06
+    # variables used to compute chirp time
+    m = m1 + m2
+    eta = m1 * m2 / m / m
+    c0T = c2T = c3T = c4T = c5T = c6T = c6LogT = c7T = 0.0
+
+    c7T = Pi * (
+        14809.0 * eta * eta / 378.0 - 75703.0 * eta / 756.0 - 15419335.0 / 127008.0
+    )
+
+    c6T = (
+        Gamma * 6848.0 / 105.0
+        - 10052469856691.0 / 23471078400.0
+        + Pi * Pi * 128.0 / 3.0
+        + eta * (3147553127.0 / 3048192.0 - Pi * Pi * 451.0 / 12.0)
+        - eta * eta * 15211.0 / 1728.0
+        + eta * eta * eta * 25565.0 / 1296.0
+        + eta * eta * eta * 25565.0 / 1296.0
+        + jnp.log(4.0) * 6848.0 / 105.0
+    )
+    c6LogT = 6848.0 / 105.0
+
+    c5T = 13.0 * Pi * eta / 3.0 - 7729.0 * Pi / 252.0
+
+    c4T = 3058673.0 / 508032.0 + eta * (5429.0 / 504.0 + eta * 617.0 / 72.0)
+    c3T = -32.0 * Pi / 5.0
+    c2T = 743.0 / 252.0 + eta * 11.0 / 3.0
+    c0T = 5.0 * m * MTSUN_SI / (256.0 * eta)
+
+    # This is the PN parameter v evaluated at the lower freq. cutoff
+    xT = jnp.power(Pi * m * MTSUN_SI * fmin, 1.0 / 3.0)
+    x2T = xT * xT
+    x3T = xT * x2T
+    x4T = x2T * x2T
[…]

### 2024-11-22 gwsnr/multiprocessing_routine.py

@@ -58,7 +58,7 @@ def noise_weighted_inner_prod(params):
             sampling_frequency
         params[19] : int
             index tracker
-        psds_list[20] : list
+        params[20] : list
             list of psds for each detector
         detector_list[21:] : list
             list of detectors
@@ -116,6 +116,7 @@ def noise_weighted_inner_prod(params):
 
         # need to compute the inner product for
         p_array = psds_objects[det].get_power_spectral_density_array(waveform_generator.frequency_array)
+
         idx2 = (p_array != 0.0) & (p_array != np.inf)
         hp_inner_hp = noise_weighted_inner_product(
             polas["plus"][idx2],
@@ -142,3 +143,92 @@ def noise_weighted_inner_prod(params):
         hc_inner_hc_list.append(hc_inner_hc)
 
     return (hp_inner_hp_list, hc_inner_hc_list, params[19])
+
+
+def noise_weighted_inner_prod_ripple(params):
+    """
+        Probaility of detection of GW for the given sensitivity of the detectors
+
+        Parameters
+        ----------
+        params : list
+            list of parameters for the inner product calculation
+            List contains: \n
+            params[0] : `numpy.ndarray`
+                plus polarization
+            params[1] : `numpy.ndarray`
+                cross polarization
+            params[2] : `numpy.ndarray`
+                frequency array
+            params[3] : `float`
+                cutt-off size of given arrays
+            params[4] : `float`
+                minimum frequency
+            params[5] : `float`
+                duration
+            params[6] : `int`
+                index
+            params[7] : `list` 
+                psd objects of given detectors
+
+        Returns
+        -------
+        SNRs_list : list
+            contains opt_snr for each detector and net_opt_snr
+        params[19] : int
+            index tracker
+    """
+
+    ## input 
+    hp = params[0]
+    hc = params[1]
+    fs = params[2]
+    fsize = params[3]
+    fmin = params[4]
+    duration = params[5]
+
+    # for i in range(size):
+    # remove the np.nan padding
+    hp = np.array(hp[:fsize])
+    hc = np.array(hc[:fsize])
+    # find the index of 20Hz or nearby
+    # set all elements to zero below this index
+    fs =  fs[:fsize]
+    idx = np.abs( fs - fmin).argmin()
+    hp[:idx] = 0.0 + 0.0j
[…]

### 2024-11-22 gwsnr/njit_functions.py

@@ -4,7 +4,7 @@ Helper functions for gwsnr. All functions are njit compiled.
 """
 
 import numpy as np
-from numba import njit
+from numba import njit, jit
 
 Gamma = 0.5772156649015329
 Pi = np.pi
@@ -492,3 +492,62 @@ def coefficients_generator(y1, y2, y3, y4, z1, z2, z3, z4):
     matrixC = np.array([z1, z2, z2, z3, z3, z4, 0, 0, 0, 0, 0, 0])
     return np.dot(np.linalg.inv(matrixA), matrixC)
 
+@njit
+def linear_interpolator(xnew, coefficients, x, bounds_error=False, fill_value=None):
+    """
+    """
+
+    idx_max = len(x)-1
+    if bounds_error:
+        if (xnew < x[0]) or (xnew > x[idx_max]):
+            raise ValueError("Chosen x values out of bound")
+
+    # Handling extrapolation
+    i = np.searchsorted(x, xnew) - 1 
+    idx1 = xnew <= x[0]
+    i[idx1] = 0
+    idx2 = xnew > x[idx_max]
+    i[idx2] = idx_max - 1
+
+    # Calculate the relative position within the interval
+    dx = xnew - x[i]
+
+    # Calculate the interpolated value
+    # linear polynomial: a + b*dx 
+    const, slope = coefficients[i].T
+    ynew = const + slope*dx
+
+    if fill_value is not None:
+        ynew[idx1] = fill_value
+        ynew[idx2] = fill_value
+
+    return ynew
+
+@njit
+def coefficients_generator_linear(x, y):
+    """
+    """
+
+    lenx = len(x)
+    x2 = x[1:lenx]
+    x1 = x[0:lenx-1]
+    y2 = y[1:lenx]
+    y1 = y[0:lenx-1]
+
+    slope = (y2-y1)/(x2-x1)
+    const = y1
+
+    return const,slope
+
+# @njit
+# def _helper_hphc(hp,hc,fsize_arr,fs,size,f_l,i):
+#     # remove the np.nan padding
+#     hp_ = np.array(hp[i][:fsize_arr[i]], dtype=np.complex128)
+#     hc_ = np.array(hc[i][:fsize_arr[i]], dtype=np.complex128)
+#     # find the index of 20Hz or nearby
+#     # set all elements to zero below this index
+#     idx = np.abs(fs[i] - f_l).argmin()
[…]

### 2024-11-22 gwsnr/ripple_class.py

@@ -1,0 +1,380 @@
+import numpy as np
+import jax.numpy as jnp
+from ripple import ms_to_Mc_eta
+from jax import vmap
+from jax import jit
+from .njit_functions import noise_weighted_inner_product
+from .jaxjit_functions import findchirp_chirptime_jax
+import bilby
+from multiprocessing import Pool
+from tqdm import tqdm
+
+from .multiprocessing_routine import noise_weighted_inner_prod_ripple
+
+class RippleInnerProduct:
+    """
+    Class to compute the noise weighted inner product for a given waveform and PSD
+
+    Parameters
+    ----------
+    waveform_name: `str`
+        The name of the waveform to use. Ripple supported waveforms are as follows, along with corresponding required arguments: 
+        IMRPhenomXAS (aligned spin): theta = ['Mchirp', 'eta', 'a_1', 'a_2', 'luminosity_distance', 'tc', 'phase', 'theta_jn']
+        IMRPhenomD (aligned spin): theta = ['Mchirp', 'eta', 'a_1', 'a_2', 'luminosity_distance', 'tc', 'phase', 'theta_jn']
+        IMRPhenomPv2 (Still finalizing sampling checks): not known
+        TaylorF2 with tidal effects : ['Mchirp', 'eta', 'a_1', 'a_2', 'lambda_1', 'lambda_2','luminosity_distance', 'tc', 'phase', 'theta_jn']
+            lambda_1: Dimensionless tidal deformability of the primary object [between 0 and 5000]
+            lambda_2: Dimensionless tidal deformability of the secondary object [between 0 and 5000]
+        IMRPhenomD_NRTidalv2, verified for the low spin regime (a_1, a_2 < 0.05), further testing is required for higher spins: ['Mchirp', 'eta', 'a_1', 'a_2', 'lambda_1', 'lambda_2','luminosity_distance', 'tc', 'phase', 'theta_jn']
+        Note: keep tc=0.0s
+    minimum_frequency: `float`
+        Default is 20.0 Hz
+    sampling_frequency: `float`
+        Default is 2048.0 Hz
+    reference_frequency: `float`
+        Default is minimum_frequency
+
+    Waveform argument descriptions:\n
+    +--------------------+--------------+--------------------------------------+
+    | Parameter          | Units        | Description                          |
+    +====================+==============+======================================+
+    | Mchirp             | Solar Mass   | Chirp mass                           |
+    +--------------------+--------------+--------------------------------------+
+    | eta                |              | Symmetric mass ratio                 |
[…]

### 2024-11-22 gwsnr/utils.py

@@ -14,6 +14,7 @@ from importlib import resources
 import pickle
 import numpy as np
 import bilby
+from gwpy.timeseries import TimeSeries
 
 class NumpyEncoder(json.JSONEncoder):
     """
@@ -309,7 +310,30 @@ def dealing_with_psds(psds=None, ifos=None, f_min=20.0, sampling_frequency=2048.
                     "psd file name should end with either 'psd.txt' or 'asd.txt'"
                 )
 
-            detector_tensor_list.append(ifos[i].detector_tensor)
+        elif isinstance(psds[det], float):
+            duration = 16
+            sample_rate = 2048
+            psd_duration = duration * 32
+            analysis_start = psds[det]
+            psd_start_time = analysis_start - psd_duration
+
+            # set up empty interferometer
+            X1 = bilby.gw.detector.get_empty_interferometer(det)
+
+            # download the data
+            X1_psd_data = TimeSeries.fetch_open_data(
+                det, psd_start_time, psd_start_time + psd_duration, sample_rate=sample_rate, cache=True)
+
+            # calculate the psd
+            psd_alpha = 2 * X1.strain_data.roll_off / duration
+            X1_psd = X1_psd_data.psd(fftlength=duration, overlap=0, window=("tukey", psd_alpha), method="median")
+
+            # initialize the psd
+            psds_list.append(
+                bilby.gw.detector.PowerSpectralDensity(
+                    frequency_array=X1_psd.frequencies.value, psd_array=X1_psd.value
+                )
+            )
 
         elif isinstance(psds[det], str):
             try:
@@ -320,6 +344,8 @@ def dealing_with_psds(psds=None, ifos=None, f_min=20.0, sampling_frequency=2048.
                 raise ValueError(error_msg)
         else:
             raise ValueError(error_msg)
+        
+        detector_tensor_list.append(ifos[i].detector_tensor)
 
     return psds_list, detector_tensor_list, detector_list
 

### 2024-11-22 setup.py

@@ -39,5 +39,6 @@ setup(name='gwsnr',
         "tensorflow>=2.17.0,<2.18.0",
         "scikit-learn==1.5.0",
         "numexpr>=2.8.4",
+        "ripplegw",
       ]
      )

### 2024-11-24 arxiv/paper.tex
mac

@@
     polarization angles (\(\psi\)), right ascension (\(\alpha\)), and
-    declination (\(\delta\)), refer to Eqn(D1) of Allen et al. (2012).
+    declination (\(\delta\)); refer to Eqn(D1) of Allen et al. (2012).
     \(f\) is the frequency, \(f_{ISCO}\) is the last stable orbit
@@
 
-Designed for SNR calculations in systems characterized by frequency
-domain waveforms in \emph{\texttt{lalsimulation}} (LIGO Scientific
+This method is tailored for SNR calculations using frequency domain
+waveforms as defined in \emph{\texttt{lalsimulation}} (LIGO Scientific
 Collaboration, Virgo Collaboration, and KAGRA Collaboration (2018)),
-including spin-precessing binary systems.
+including spin-precessing binary systems. \texttt{gwsnr} also supports
+JAX assited inner product, where the waveform generation is facilitated
+through the \texttt{ripple} package (Edwards et al. (2024)). Key
+functions are optimized using \texttt{jax.jit} and parallelized with
+\texttt{jax.vmap}.
 
@@
 
+\bibitem[\citeproctext]{ref-Edwards:2023sak}
+Edwards, Thomas D. P., Kaze W. K. Wong, Kelvin K. H. Lam, Adam Coogan,
+Daniel Foreman-Mackey, Maximiliano Isi, and Aaron Zimmerman. 2024.
+{``{Differentiable and hardware-accelerated waveforms for gravitational
+wave data analysis}.''} \emph{Phys. Rev. D} 110 (6): 064028.
+\url{https://doi.org/10.1103/PhysRevD.110.064028}.
+
 \bibitem[\citeproctext]{ref-Gerosa:2020}

### 2025-02-13 arxiv/arxiv/paper.tex
mac

--- 2024-11-24 arxiv/paper.tex
@@
 \fancyfoot[L]{\parbox[t]{0.98\headwidth}{\footnotesize{\sffamily Hemantakumar Phurailatpam, Otto Akseli Hannuksela, (2024). \texttt{gwsnr}:
-A Python Package for Efficient SNR Calculation of
-GWs. \textit{PendingJournal of Open Source Software}, Pending(Pending), Pending. \url{https://doi.org/10.xxxxxx/draft}}}}
+A python package for efficient signal-to-noise calculation of
+gravitational-waves. \textit{PendingJournal of Open Source Software}, Pending(Pending), Pending. \url{https://doi.org/10.xxxxxx/draft}}}}
 
@@
 \hypersetup{unicode=true,
-            pdftitle={gwsnr: A Python Package for Efficient SNR Calculation of GWs},
+            pdftitle={gwsnr: A python package for efficient signal-to-noise calculation of
+gravitational-waves},
             pdfborder={0 0 0},
@@
 
-\title{\texttt{gwsnr}: A Python Package for Efficient SNR Calculation of
-GWs}
+\title{\texttt{gwsnr}: A python package for efficient signal-to-noise calculation of
+gravitational-waves}
 
-        \author[1]{Phurailatpam Hemantakumar}
+        \author[1]{Hemantakumar Phurailatpam}
           \author[1]{Otto Akseli HANNUKSELA}
@@
 
-  {\bfseries Submitted:} 3rd July 2024\\
-  {\bfseries Published:} 3rd July 2024
+  {\bfseries Submitted:} 13th Dec 2024\\
+  {\bfseries Published:}
 
@@
 theory of General Relativity, have revolutionized astrophysics since
-their first detection in 2015 (Abbott, B. P. et al. (2016a)). These
+their first detection in 2015 (Abbott, B.P. et al. (2016a)). These
 waves are emitted by cataclysmic events like the merging of binary black
@@
 is pivotal in confirming the detection of GWs and extracting
-astrophysical information from them (Abbott, B. P. et al. (2016b)).
+astrophysical information from them (Abbott, B.P. et al. (2016b)).
 However, specific scenarios in GW research, particularly in simulations
@@
 The \emph{\texttt{gwsnr}} Python package addresses the need for
-efficient SNR computation in GW research. It innovatively streamlines
-SNR calculations, enhancing accuracy and efficiency with several
-advanced techniques. Firstly, it utilizes an innovative interpolation
+efficient SNR computation in GW research. It provides a flexible and
+user-friendly interface, allowing users to combine various detector
+noise models, waveform models, detector configurations, and signal
+parameters. \emph{\texttt{gwsnr}} enhances SNR calculations through
+several key features. Firstly, it utilizes an innovative interpolation
 method, employing a partial-scaling approach for accurately
-interpolating the SNR of GWs from spin-less binary systems wrt to their
-mass parameters. Secondly, the package features a noise-weighted inner
-product method, similar to that in the \emph{\texttt{bilby}} package
-(Ashton, Gregory et al. (2022)), but enhanced with multiprocessing
-capabilities. This integration allows for the parallel processing of
-complex calculations, thereby expediting the SNR computation. Thirdly, a
-trained Artificial Neural Network (ANN) model is incorporated for rapid
-`probability of detection' (Pdet) estimation for BBH systems with spin
-precession. Lastly, \emph{\texttt{gwsnr}} leverages the
-\emph{\texttt{numba}}'s Just-In-Time (njit) compiler (Lam, Pitrou, and
-Seibert (2022)), which optimizes performance by compiling Python code
-into machine code at runtime, drastically reducing execution times.
-Beyond these technical merits, \emph{\texttt{gwsnr}} stands out for its
-user-friendly features and seamless integration with other related
-software packages, making it not just a powerful tool but also an
-accessible one for researchers. These attributes position
-\emph{\texttt{gwsnr}} as an invaluable asset in GW data analysis,
-particularly in simulations of detectable compact binary mergers,
-determining rates of GW events, related to both lensed and un-lensed
-events (Phurailatpam et al. (2024), Ng et al. (2024)), and in the
-analysis of selection effects within hierarchical Bayesian frameworks
-(Thrane and Talbot (2019)). The package thus represents a significant
-step forward in aiding GW research, enabling more precise and efficient
-exploration of the universe through GW observations and simulations.
-Additionally, \emph{\texttt{gwsnr}} is instrumental in the
-\emph{\texttt{ler}} (Phurailatpam et al. (2024)) package for calculating
-detectable rates of both lensed and unlensed GW events, showcasing its
-utility in advanced GW studies.
+interpolating the SNR of GWs from spin-less binary systems. Secondly,
+the package features a noise-weighted inner product method, similar to
+that in the \emph{\texttt{bilby}} package (Ashton, Gregory et al.
+(2022)), but enhanced with multiprocessing capabilities. This parallel
+processing is crucial for handling large datasets and computationally
+intensive analyses. Thirdly, a trained Artificial Neural Network (ANN)
+model is incorporated for rapid `probability of detection' (Pdet)
+estimation for BBH systems with spin precession. Lastly,
+\emph{\texttt{gwsnr}} leverages the \emph{\texttt{numba}}'s Just-In-Time
+(njit) compiler (Lam, Pitrou, and Seibert (2022)), which optimizes
+performance by compiling Python code into machine code at runtime,
+drastically reducing execution times. This combination of advanced
+techniques and user-friendly design makes gwsnr a valuable tool for GW
+data analysis, particularly in simulating detectable compact binary
+mergers, determining rates of both lensed and unlensed GW events (as
+demonstrated by its use in the \emph{\texttt{ler}} package; Phurailatpam
+et al. (2024), Ng et al. (2024)), and will help in the analysis of
+selection effects within hierarchical Bayesian frameworks (Thrane and
+Talbot (2019)).
 
@@
 
+In addition to providing trained ANN models for specific configurations,
+\emph{\texttt{gwsnr}} offers users the flexibility to develop and train
+custom models tailored to their unique requirements. This adaptability
+allows for optimization based on variations in detector sensitivity,
+gravitational wave properties, and other research-specific factors,
+ensuring maximum model effectiveness across different scenarios.
+
 \section{Acknowledgements}\label{acknowledgements}
@@
 
-\section*{References}\label{references}
+\hypertarget{references}{%
+\section*{References}\label{references}}
 \addcontentsline{toc}{section}{References}
 
-\phantomsection\label{refs}
-\begin{CSLReferences}{1}{0}
-\bibitem[\citeproctext]{ref-tensorflow2015}
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-tensorflow2015}
 Abadi, Martín, Ashish Agarwal, Paul Barham, Eugene Brevdo, Zhifeng Chen,
@@
 
-\bibitem[\citeproctext]{ref-Abbott:2016:rates}
+\leavevmode\hypertarget{ref-Abbott:2016:rates}
 Abbott, B. P., R. Abbott, T. D. Abbott, M. R. Abernathy, F. Acernese, K.
@@
 
-\bibitem[\citeproctext]{ref-Abbott:2016}
-Abbott, B. P., R. Abbott, T. D. Abbott, M. R. Abernathy, F. Acernese, K.
+\leavevmode\hypertarget{ref-Abbott:2016}
+Abbott, B.P., R. Abbott, T.D. Abbott, M.R. Abernathy, F. Acernese, K.
 Ackley, C. Adams, et al. 2016a. {``Observation of Gravitational Waves
@@
 
-\bibitem[\citeproctext]{ref-Abbott:2016:detection}
-Abbott, B. P., R. Abbott, T. D. Abbott, M. R. Abernathy, F. Acernese, K.
+\leavevmode\hypertarget{ref-Abbott:2016:detection}
+Abbott, B.P., R. Abbott, T.D. Abbott, M.R. Abernathy, F. Acernese, K.
 Ackley, C. Adams, et al. 2016b. {``GW150914: First Results from the
@@
 
-\bibitem[\citeproctext]{ref-Abbott2020}
+\leavevmode\hypertarget{ref-Abbott2020}
 Abbott, B. P., R. Abbott, T. D. Abbott, S. Abraham, F. Acernese, K.
@@
 
-\bibitem[\citeproctext]{ref-virgo:2019}
+\leavevmode\hypertarget{ref-virgo:2019}
 Acernese, F., M. Agathos, L. Aiello, A. Allocca, A. Amato, S. Ansoldi,
@@
 
-\bibitem[\citeproctext]{ref-VIRGO2015}
+\leavevmode\hypertarget{ref-VIRGO2015}
 Acernese, F, M Agathos, K Agatsuma, D Aisa, N Allemandou, A Allocca, J
@@
 
-\bibitem[\citeproctext]{ref-akutsu2020overviewkagradetectordesign}
+\leavevmode\hypertarget{ref-akutsu2020overviewkagradetectordesign}
 Akutsu, T., M. Ando, K. Arai, Y. Arai, S. Araki, A. Araya, N. Aritomi,
@@
 
-\bibitem[\citeproctext]{ref-Allen:2012}
+\leavevmode\hypertarget{ref-Allen:2012}
 Allen, Bruce, Warren G. Anderson, Patrick R. Brady, Duncan A. Brown, and
@@
 
-\bibitem[\citeproctext]{ref-bilby}
+\leavevmode\hypertarget{ref-bilby}
 Ashton, Gregory, Sylvia Biscoveanu, Neil Cornish, Isaac Dal Canto,
@@
 
-\bibitem[\citeproctext]{ref-PhysRevD:88:043007}
+\leavevmode\hypertarget{ref-PhysRevD:88:043007}
 Aso, Yoichi, Yuta Michimura, Kentaro Somiya, Masaki Ando, Osamu
@@
 
-\bibitem[\citeproctext]{ref-PhysRevD.102.062003}
+\leavevmode\hypertarget{ref-PhysRevD.102.062003}
 Buikema, A., C. Cahillane, G. L. Mansell, C. D. Blair, R. Abbott, C.
@@
 
-\bibitem[\citeproctext]{ref-ChapmanBird2023}
+\leavevmode\hypertarget{ref-ChapmanBird2023}
 Chapman-Bird, Christian E A et al. 2023. {``Rapid Determination of LISA
@@
 
-\bibitem[\citeproctext]{ref-Edwards:2023sak}
+\leavevmode\hypertarget{ref-Edwards:2023sak}
 Edwards, Thomas D. P., Kaze W. K. Wong, Kelvin K. H. Lam, Adam Coogan,
@@
 
-\bibitem[\citeproctext]{ref-Gerosa:2020}
+\leavevmode\hypertarget{ref-Gerosa:2020}
 Gerosa, Davide et al. 2020. {``Gravitational-Wave Selection Effects
@@
 
-\bibitem[\citeproctext]{ref-numba}
+\leavevmode\hypertarget{ref-numba}
 Lam, Stan, Stéphane Pitrou, and Mark Seibert. 2022. {``Numba: A High
@@
 
-\bibitem[\citeproctext]{ref-lalsuite}
+\leavevmode\hypertarget{ref-lalsuite}
 LIGO Scientific Collaboration, Virgo Collaboration, and KAGRA
@@
 
-\bibitem[\citeproctext]{ref-ng2024}
+\leavevmode\hypertarget{ref-ng2024}
 Ng, Leo C. Y., Justin Janquart, Hemantakumar Phurailatpam, Harsh Narola,
@@
 
-\bibitem[\citeproctext]{ref-scikitlearn}
+\leavevmode\hypertarget{ref-scikitlearn}
 Pedregosa, Fabian, Gaël Varoquaux, Alexandre Gramfort, Vincent Michel,
@@
 
-\bibitem[\citeproctext]{ref-ler}
+\leavevmode\hypertarget{ref-ler}
 Phurailatpam, Hemantakumar, Anupreeta More, Harsh Narola, Ng Chung Yin,
@@
 
-\bibitem[\citeproctext]{ref-Taylor:2018}
+\leavevmode\hypertarget{ref-Taylor:2018}
 Taylor, Stephen R., and Davide Gerosa. 2018. {``Mining
@@
 
-\bibitem[\citeproctext]{ref-LIGO2015}
+\leavevmode\hypertarget{ref-LIGO2015}
 The LIGO Scientific Collaboration, J Aasi, B P Abbott, R Abbott, T
@@
 
-\bibitem[\citeproctext]{ref-Thrane:2019}
+\leavevmode\hypertarget{ref-Thrane:2019}
 Thrane, Eric, and Colm Talbot. 2019. {``An Introduction to Bayesian
@@
 
-\end{CSLReferences}
-
 \end{document}

### 2025-02-13 docs_old/conf.py

@@ -1,147 +1,0 @@
-# Configuration file for the Sphinx documentation builder.
-#
-# This file only contains a selection of the most common options. For a full
-# list see the documentation:
-# https://www.sphinx-doc.org/en/master/usage/configuration.html
-
-# -- Path setup --------------------------------------------------------------
-
-# If extensions (or modules to document with autodoc) are in another directory,
-# add these directories to sys.path here. If the directory is relative to the
-# documentation root, use os.path.abspath to make it absolute, like shown here.
-#
-# import os
-# import sys
-# sys.path.insert(0, os.path.abspath('.'))
-
-
-# -- Project information -----------------------------------------------------
-import os
-import sys
-sys.path.insert(0, os.path.abspath('.'))
-sys.path.insert(0, os.path.abspath("../gwsnr")) 
-
-project = 'gwsnr'
-copyright = '2023, Phurailatpam Hemantakumar'
-author = 'Phurailatpam Hemantakumar'
-release = '0.3.2'
-
-
-# -- General configuration ---------------------------------------------------
-
-# Add any Sphinx extension module names here, as strings. They can be
-# extensions coming with Sphinx (named 'sphinx.ext.*') or your custom
-# ones.
-extensions = [
-    "nbsphinx",
-    "sphinx.ext.mathjax",
-    "numpydoc",
-    "sphinx.ext.autosummary",
-    "sphinx.ext.autosectionlabel",
-    "sphinx.ext.inheritance_diagram",
-    "sphinx_tabs.tabs",
-    "sphinx.ext.viewcode",
-    "sphinx.ext.intersphinx",
-    "sphinx.ext.napoleon",
-    "sphinx_copybutton",
-    "autoapi.extension",
-]
-
-# Add any paths that contain templates here, relative to this directory.
-templates_path = ['_templates']
-exclude_patterns = ['_build', 'Thumbs.db', '.DS_Store', '.ipynb_checkpoints','.ipynb', "venv", ".*", '**.ipynb_checkpoints', '**/*.ipynb_checkpoints', '**/**/*.ipynb_checkpoints', '**/**/**/*.ipynb_checkpoints']
-autodoc_member_order = 'bysource'
-numpydoc_show_class_members = False
-autoapi_add_toctree_entry = False
-# -- Napoleon options
-napoleon_include_special_with_doc = True
-pygments_style = 'sphinx'
-
-# Don't mess with double-dash used in CLI options
-smartquotes_action = "qe"
-
-# -- Options for HTML output -------------------------------------------------
[…]

### 2025-02-13 gwsnr/__init__.py

@@ -13,6 +13,11 @@ __version__ = "0.3.2"
 import os
 __file__ = os.path.abspath(__file__)
 
+# import warnings
+# warnings.filterwarnings("ignore", "Wswiglal-redir-stdio")
+# import lal
+# lal.swig_redirect_standard_output_error(False)
+
 # import multiprocessing as mp
 
 # def set_multiprocessing_start_method():
@@ -38,6 +43,7 @@ from .multiprocessing_routine import *
 from .utils import *
 from .ripple_class import *
 from .jaxjit_functions import *
+from .ann_model_generator import *
 
 from . import ann
 

### 2025-02-13 gwsnr/ann_model_generator.py

@@ -1,0 +1,482 @@
+# -*- coding: utf-8 -*-
+"""
+This module contains the ANNModelGenerator class which is used to generate the ANN (Artificial Neural Network) model that can be used to predict the SNR of the GW events.
+"""
+
+import numpy as np
+import os
+import pickle
+from .gwsnr import GWSNR
+from .utils import append_json, get_param_from_json, load_json, load_pickle, save_pickle, load_ann_h5
+from scipy.optimize import curve_fit
+
+from gwsnr import antenna_response_array, cubic_spline_interpolator2d
+import tensorflow as tf
+from sklearn.preprocessing import StandardScaler
+from sklearn.model_selection import train_test_split
+from sklearn.metrics import confusion_matrix, accuracy_score
+
+class ANNModelGenerator():
+    """
+    ANNModelGenerator class is used to generate the ANN model that can be used to predict the SNR of the GW events.
+
+    Parameters
+    ----------
+    npool : `int`
+        Number of processors to use for parallel processing.
+        Default is 4.
+    gwsnr_verbose : `bool`
+        If True, print the progress of the GWSNR calculation.
+        Default is True.
+    snr_th : `float`
+        SNR threshold for the error calculation.
+        Default is 8.0.
+    waveform_approximant : `str`
+        Waveform approximant to be used for the GWSNR calculation and the ANN model.
+        Default is "IMRPhenomXPHM".
+    **kwargs : `dict`
+        Keyword arguments for the GWSNR class.
+        To see the list of available arguments, 
+        >>> from gwsnr import GWSNR
+        >>> help(GWSNR)
+        
+    Examples
+    --------
+    >>> from gwsnr import ANNModelGenerator
+    >>> amg = ANNModelGenerator()
+    >>> amg.ann_model_training(gw_param_dict='gw_param_dict.json') # training the ANN model with pre-generated parameter points
+
+    """
+    
+    def __init__(self,
+        directory="./ler_data",
+        npool=4,
+        gwsnr_verbose=True,
+        snr_th=8.0,
+        waveform_approximant="IMRPhenomXPHM",
+        **kwargs,  # ler and gwsnr arguments
+    ):
+
+        self.directory = directory
+        self.ann_model = self.ann_model_4layers
+        self.ann = None
+        self.scaler = None
+
+        self.gwsnr_args = dict(
[…]

### 2025-02-13 gwsnr/gwsnr.py

@@ -31,6 +31,7 @@ from .utils import (
     load_ann_h5,
     load_pickle_from_module,
     load_json_from_module,
+    get_gw_parameters,
 )
 from .njit_functions import (
     get_interpolated_snr,
@@ -308,9 +309,10 @@ class GWSNR:
         pdet=False,
         snr_th=8.0,
         snr_th_net=8.0,
-        ann_path_dict=None
+        ann_path_dict=None,
     ):
 
+        print("\nInitializing GWSNR class...\n")
         # setting instance attributes
         self.npool = npool
         self.pdet = pdet
@@ -524,25 +526,31 @@ class GWSNR:
             if not os.path.exists(ann_path_dict[detector]['model_path']):
                 # load the model from gwsnr/ann directory
                 model_dict[detector] = load_ann_h5_from_module('gwsnr', 'ann', ann_path_dict[detector]['model_path'])
+                print(f"ANN model for {detector} is loaded from gwsnr/ann directory.")
             else:
                 # load the model from the given path
                 model_dict[detector] = load_ann_h5(ann_path_dict[detector]['model_path'])
+                print(f"ANN model for {detector} is loaded from {ann_path_dict[detector]['model_path']}.")
 
             # get ann scaler
             if not os.path.exists(ann_path_dict[detector]['scaler_path']):
                 # load the scaler from gwsnr/ann directory
                 scaler_dict[detector] = load_pickle_from_module('gwsnr', 'ann', ann_path_dict[detector]['scaler_path'])
+                print(f"ANN scaler for {detector} is loaded from gwsnr/ann directory.")
             else:
                 # load the scaler from the given path
                 scaler_dict[detector] = load_pickle(ann_path_dict[detector]['scaler_path'])
+                print(f"ANN scaler for {detector} is loaded from {ann_path_dict[detector]['scaler_path']}.")
 
             # get error_adjustment
             if not os.path.exists(ann_path_dict[detector]['error_adjustment_path']):
                 # load the error_adjustment from gwsnr/ann directory
                 error_adjustment[detector] = load_json_from_module('gwsnr', 'ann', ann_path_dict[detector]['error_adjustment_path'])
[…]

### 2025-02-13 gwsnr/njit_functions.py

@@ -395,12 +395,14 @@ def cubic_spline_interpolator2d(xnew, ynew, coefficients, x, y):
     """
 
     len_y = len(y)
-    # y_idx = np.searchsorted(y, ynew)
-
+    # find the index nearest to the ynew in y
     y_idx = np.searchsorted(y, ynew) - 1 if ynew > y[0] else 0
-    # result = cubic_spline_interpolator(xnew, coefficients[y_idx], x)
 
-    if y_idx == 0:  # lower end point
+    if (ynew>y[0]) and (ynew<y[1]):
+        if ynew > y[y_idx] + (y[y_idx+1] - y[y_idx]) / 2:
+            y_idx = y_idx + 1
+        result = cubic_spline_interpolator(xnew, coefficients[y_idx], x)
+    elif y_idx == 0:  # lower end point
         result = cubic_spline_interpolator(xnew, coefficients[0], x)
         # print("a")
     elif y_idx+1 == len_y:  # upper end point

### 2025-02-13 gwsnr/utils.py

@@ -8,7 +8,7 @@ import json
 # supress warning
 import absl.logging
 absl.logging.set_verbosity(absl.logging.ERROR)
-os.environ['TF_CPP_MIN_LOG_LEVEL'] = '3' 
+os.environ['TF_CPP_MIN_LOG_LEVEL'] = '3'
 from tensorflow.keras.models import load_model
 from importlib import resources
 import pickle
@@ -45,7 +45,6 @@ def save_json(file_name, param):
             json.dump(param, write_file)
         except:
             json.dump(param, write_file, indent=4, cls=NumpyEncoder)
-
 
 def load_json(file_name):
     """Load a json file.
@@ -110,6 +109,149 @@ def load_ann_h5(filename):
     """
 
     return load_model(filename)
+
+def append_json(file_name, new_dictionary, old_dictionary=None, replace=False):
+    """
+    Append (values with corresponding keys) and update a json file with a dictionary. There are four options:
+
+    1. If old_dictionary is provided, the values of the new dictionary will be appended to the old dictionary and save in the 'file_name' json file.
+    2. If replace is True, replace the json file (with the 'file_name') content with the new_dictionary.
+    3. If the file does not exist, create a new one with the new_dictionary.
+    4. If none of the above, append the new dictionary to the content of the json file.
+
+    Parameters
+    ----------
+    file_name : `str`
+        json file name for storing the parameters. 
+    new_dictionary : `dict`
+        dictionary to be appended to the json file.
+    old_dictionary : `dict`, optional
+        If provided the values of the new dictionary will be appended to the old dictionary and save in the 'file_name' json file. 
+        Default is None.
+    replace : `bool`, optional
+        If True, replace the json file with the dictionary. Default is False.
+
+    """
+
+    # check if the file exists
+    # time
+    # start = datetime.datetime.now()
+    if old_dictionary:
+        data = old_dictionary
+    elif replace:
+        data = new_dictionary
+    elif not os.path.exists(file_name):
+        #print(f" {file_name} file does not exist. Creating a new one...")
+        replace = True
+        data = new_dictionary
+    else:
+        #print("getting data from file")
+        with open(file_name, "r", encoding="utf-8") as f:
+            data = json.load(f)
+    # end = datetime.datetime.now()
+    # print(f"Time taken to load the json file: {end-start}")
+
+    # start = datetime.datetime.now()
+    if not replace:
[…]

### 2025-02-13 setup.py

@@ -34,7 +34,7 @@ setup(name='gwsnr',
         "tqdm>=4.64.0",
         "gwpy>=2.1.5",
         "h5py>=3.11.0,<3.12.0",
-        #"numba>=0.57.1,<0.58.0",
+        "numba>=0.57.1,<0.58.0",
         "numba>=0.57.1",
         "tensorflow>=2.17.0,<2.18.0",
         "scikit-learn==1.5.0",

### 2025-06-21 examples/snr_generation.py
mac

@@ -1,7 +1,7 @@
 """
 This script generates a set of BBH (Binary Black Hole) parameters and calculates the optimal SNR (Signal-to-Noise Ratio) for each set of parameters. The parameters are saved in a json file.
 """
-
+ENABLE_PJRT_COMPATIBILITY=1
 import numpy as np
 from gwsnr import GWSNR
 from gwsnr.utils import save_json
@@ -43,16 +43,32 @@ theta_jn = np.random.uniform(0,2*np.pi, size=nsamples)
 ra, dec, psi, phase = np.random.uniform(0,2*np.pi, size=nsamples), np.random.uniform(0,np.pi, size=nsamples), np.random.uniform(0,2*np.pi, size=nsamples), np.random.uniform(0,2*np.pi, size=nsamples)
 a_1, a_2, tilt_1, tilt_2, phi_12, phi_jl = 0,0,0,0,0,0 # Zero spin
 
-# Calculate the optimal SNR (Signal-to-Noise Ratio) for each set of parameters
-# with interpolation
-interp_snr = gwsnr.snr(mass_1=mass_1, mass_2=mass_1, luminosity_distance=luminosity_distance, theta_jn=theta_jn, psi=psi, phase=phase, ra=ra, dec=dec)
-
-# save the SNR and BBH parameters
 # create a dictionary
 data = {'mass_1': mass_1, 'mass_2': mass_2, 'luminosity_distance': luminosity_distance, 'theta_jn': theta_jn, 'psi': psi, 'phase': phase, 'ra': ra, 'dec': dec}
-data.update(interp_snr)
+
+# Calculate the optimal SNR (Signal-to-Noise Ratio) for each set of parameters
+# with interpolation
+interp_snr = gwsnr.snr(**data)
+
+# save the SNR and BBH parameters
+interp_data = data.copy()
+interp_data.update(interp_snr)
 
 # save the dictionary in json format
-file_name = './snr_data.json'
-print(f'saving results as json file at {file_name}')
-save_json(file_name, data);
+file_name = './interpolated_snr_data.json'
+print(f'saving interpolated SNR results as json file at {file_name}')
+save_json(file_name, interp_data);
+
+# Calculate the optimal SNR (Signal-to-Noise Ratio) for each set of parameters
+# with inner product
+bilby_snr = gwsnr.compute_bilby_snr(**data)
+
+# save the SNR and BBH parameters
+bilby_data = data.copy()
+bilby_data.update(bilby_snr)
+
[…]

### 2025-06-21 gwsnr/__init__.py

@@ -18,31 +18,32 @@ __file__ = os.path.abspath(__file__)
 # import lal
 # lal.swig_redirect_standard_output_error(False)
 
-import multiprocessing as mp
-def set_multiprocessing_start_method():
-    if os.name == 'posix':  # posix indicates the program is run on Unix/Linux/MacOS
-      try:
-         mp.set_start_method('fork', force=True)
-      except RuntimeError:
-         # The start method can only be set once and must be set before any process starts
-         pass
-    else:
-      # For Windows and other operating systems, use 'spawn'
-      try:
-         mp.set_start_method('spawn', force=True)
-      except RuntimeError:
-         pass
-set_multiprocessing_start_method()
+# import multiprocessing as mp
+# def set_multiprocessing_start_method():
+#     if os.name == 'posix':  # posix indicates the program is run on Unix/Linux/MacOS
+#       try:
+#          mp.set_start_method('fork', force=True)
+#       except RuntimeError:
+#          # The start method can only be set once and must be set before any process starts
+#          pass
+#     else:
+#       # For Windows and other operating systems, use 'spawn'
+#       try:
+#          mp.set_start_method('spawn', force=True)
+#       except RuntimeError:
+#          pass
+# set_multiprocessing_start_method()
 
-from .gwsnr import *
-from .njit_functions import *
-from .multiprocessing_routine import *
-# from .pdet import *
-from .utils import *
-from .ripple_class import *
-from .jaxjit_functions import *
-from .ann_model_generator import *
+from . import core
+from .core import GWSNR
+# from .njit_functions import *
+# from .multiprocessing_routine import *
+# # from .pdet import *
+# from .utils import *
+# from .ripple_class import *
+# from .jaxjit_functions import *
+# from .ann_model_generator import *
 
-from . import ann
+# from . import ann
 
 

### 2025-06-21 gwsnr/ann/__init__.py

@@ -1,0 +1,2 @@
+from .ann_model_generator import *
+from . import data

### 2025-06-21 gwsnr/ann/ann_model_generator.py

@@ -6,11 +6,16 @@ This module contains the ANNModelGenerator class which is used to generate the A
 import numpy as np
 import os
 import pickle
-from .gwsnr import GWSNR
-from .utils import append_json, get_param_from_json, load_json, load_pickle, save_pickle, load_ann_h5
+from ..core import GWSNR
+from ..utils import append_json, get_param_from_json, load_json, load_ann_h5
 from scipy.optimize import curve_fit
+from ..numba import (
+    antenna_response_array,
+)
+import jax
+jax.config.update("jax_enable_x64", False)
+import jax.numpy as jnp
 
-from gwsnr import antenna_response_array, cubic_spline_interpolator2d
 import tensorflow as tf
 from sklearn.preprocessing import StandardScaler
 from sklearn.model_selection import train_test_split
@@ -53,6 +58,7 @@ class ANNModelGenerator():
         npool=4,
         gwsnr_verbose=True,
         snr_th=8.0,
+        snr_type="interpolation_aligned_spins_jax",
         waveform_approximant="IMRPhenomXPHM",
         **kwargs,  # ler and gwsnr arguments
     ):
@@ -66,15 +72,17 @@ class ANNModelGenerator():
             npool=npool,
             # gwsnr args
             mtot_min=2.0,
-            mtot_max=200,
+            mtot_max=439.6,
             ratio_min=0.1,
             ratio_max=1.0,
-            mtot_resolution=500,
+            spin_max=0.9,
+            mtot_resolution=200,
             ratio_resolution=50,
+            spin_resolution=20,
             sampling_frequency=2048.0,
             waveform_approximant=waveform_approximant,
             minimum_frequency=20.0,
-            snr_type="interpolation",
+            snr_type="interpolation_aligned_spins_jax",
             psds=None,
             ifos=None,
             interpolator_dir="./interpolator_pickle",
@@ -95,12 +103,14 @@ class ANNModelGenerator():
             mtot_max=self.gwsnr_args['mtot_max'],
             ratio_min=self.gwsnr_args['ratio_min'],
             ratio_max=self.gwsnr_args['ratio_max'],
+            spin_max=self.gwsnr_args['spin_max'],
             mtot_resolution=self.gwsnr_args['mtot_resolution'],
[…]

### 2025-06-21 gwsnr/core/__init__.py

@@ -1,0 +1,1 @@
+from .gwsnr import *

### 2025-06-21 gwsnr/core/gwsnr.py

@@ -4,12 +4,10 @@ This module contains functions for calculating the SNR of a CBC signal. It has t
 """
 
 import os
-import pickle
-from multiprocessing import Pool
+import multiprocessing as mp
 import numpy as np
 from tqdm import tqdm
 from scipy.stats import norm
-from scipy.interpolate import CubicSpline
 from scipy.optimize import fsolve
 
 # warning suppression lal
@@ -18,9 +16,8 @@ warnings.filterwarnings("ignore", "Wswiglal-redir-stdio")
 import lal
 lal.swig_redirect_standard_output_error(False)
 
-from .ripple_class import RippleInnerProduct
-
-from .utils import (
+from ..ripple import RippleInnerProduct
+from ..utils import (
     dealing_with_psds,
     interpolator_check,
     load_json,
@@ -33,27 +30,22 @@ from .utils import (
     load_json_from_module,
     get_gw_parameters,
 )
-import jax
-import jax.numpy as jnp
-jax.config.update("jax_enable_x64", True)
-from .njit_functions import (
-    get_interpolated_snr,
+from ..utils import noise_weighted_inner_prod
+
+from ..numba import (
     findchirp_chirptime,
     antenna_response,
     antenna_response_array,
 )
-from .jaxjit_functions import (
-    get_interpolated_snr_aligned_spins,
-    get_interpolated_snr_no_spins,
-)
-from .multiprocessing_routine import noise_weighted_inner_prod
+import jax
+import jax.numpy as jnp
+jax.config.update("jax_enable_x64", False)
 
 # defining constants
 C = 299792458.0
 G = 6.67408e-11
 Pi = np.pi
 MTSUN_SI = 4.925491025543576e-06
-
 
 class GWSNR:
     """
@@ -320,6 +312,9 @@ class GWSNR:
         snr_th=8.0,
         snr_th_net=8.0,
         ann_path_dict=None,
+        snr_recalculation=False,
+        snr_recalculation_range=[6,8],
+        snr_recalculation_waveform_approximant="IMRPhenomXPHM",
     ):
 
         print("\nInitializing GWSNR class...\n")
@@ -332,19 +327,6 @@ class GWSNR:
         self.duration_min = duration_min
         self.snr_type = snr_type
         self.spin_max = spin_max
-        # change multiprocessing start method from fork to spawn if snr_type is inner_product_jax
-        if self.snr_type == "inner_product_jax":
-            import multiprocessing as mp
-            import os
-
[…]

### 2025-06-21 gwsnr/jax/__init__.py

@@ -1,0 +1,2 @@
+from .jaxjit_functions import *
+from .jaxjit_interpolators import *

### 2025-06-21 gwsnr/jax/jaxjit_functions.py

@@ -1,0 +1,161 @@
+import jax
+jax.config.update("jax_enable_x64", False)
+import jax.numpy as jnp
+from jax import jit, vmap
+
+@jit
+def findchirp_chirptime_jax(m1, m2, fmin):
+    """
+    Time taken from f_min to f_lso (last stable orbit). 3.5PN in fourier phase considered.
+
+    Parameters
+    ----------
+    m1 : `float`
+        Mass of the first body in solar masses.
+    m2 : `float`
+        Mass of the second body in solar masses.
+    fmin : `float`
+        Lower frequency cutoff.
+
+    Returns
+    -------
+    chirp_time : float
+        Time taken from f_min to f_lso (last stable orbit frequency).
+    """
+
+    Gamma = 0.5772156649015329
+    Pi = jnp.pi
+    MTSUN_SI = 4.925491025543576e-06
+    # variables used to compute chirp time
+    m = m1 + m2
+    eta = m1 * m2 / m / m
+    c0T = c2T = c3T = c4T = c5T = c6T = c6LogT = c7T = 0.0
+
+    c7T = Pi * (
+        14809.0 * eta * eta / 378.0 - 75703.0 * eta / 756.0 - 15419335.0 / 127008.0
+    )
+
+    c6T = (
+        Gamma * 6848.0 / 105.0
+        - 10052469856691.0 / 23471078400.0
+        + Pi * Pi * 128.0 / 3.0
+        + eta * (3147553127.0 / 3048192.0 - Pi * Pi * 451.0 / 12.0)
+        - eta * eta * 15211.0 / 1728.0
+        + eta * eta * eta * 25565.0 / 1296.0
+        + eta * eta * eta * 25565.0 / 1296.0
+        + jnp.log(4.0) * 6848.0 / 105.0
+    )
+    c6LogT = 6848.0 / 105.0
+
+    c5T = 13.0 * Pi * eta / 3.0 - 7729.0 * Pi / 252.0
+
+    c4T = 3058673.0 / 508032.0 + eta * (5429.0 / 504.0 + eta * 617.0 / 72.0)
+    c3T = -32.0 * Pi / 5.0
+    c2T = 743.0 / 252.0 + eta * 11.0 / 3.0
+    c0T = 5.0 * m * MTSUN_SI / (256.0 * eta)
+
+    # This is the PN parameter v evaluated at the lower freq. cutoff
+    xT = jnp.power(Pi * m * MTSUN_SI * fmin, 1.0 / 3.0)
[…]

### 2025-06-21 gwsnr/jax/jaxjit_interpolators.py

@@ -1,166 +1,8 @@
-import numpy as np
 import jax
+jax.config.update("jax_enable_x64", False)
 import jax.numpy as jnp
 from jax import jit, vmap, lax
-jax.config.update("jax_enable_x64", True)
-
-
-@jit
-def findchirp_chirptime_jax(m1, m2, fmin):
-    """
-    Time taken from f_min to f_lso (last stable orbit). 3.5PN in fourier phase considered.
-
-    Parameters
-    ----------
-    m1 : `float`
-        Mass of the first body in solar masses.
-    m2 : `float`
-        Mass of the second body in solar masses.
-    fmin : `float`
-        Lower frequency cutoff.
-
-    Returns
-    -------
-    chirp_time : float
-        Time taken from f_min to f_lso (last stable orbit frequency).
-    """
-
-    Gamma = 0.5772156649015329
-    Pi = jnp.pi
-    MTSUN_SI = 4.925491025543576e-06
-    # variables used to compute chirp time
-    m = m1 + m2
-    eta = m1 * m2 / m / m
-    c0T = c2T = c3T = c4T = c5T = c6T = c6LogT = c7T = 0.0
-
-    c7T = Pi * (
-        14809.0 * eta * eta / 378.0 - 75703.0 * eta / 756.0 - 15419335.0 / 127008.0
-    )
-
-    c6T = (
-        Gamma * 6848.0 / 105.0
-        - 10052469856691.0 / 23471078400.0
-        + Pi * Pi * 128.0 / 3.0
-        + eta * (3147553127.0 / 3048192.0 - Pi * Pi * 451.0 / 12.0)
-        - eta * eta * 15211.0 / 1728.0
-        + eta * eta * eta * 25565.0 / 1296.0
-        + eta * eta * eta * 25565.0 / 1296.0
-        + jnp.log(4.0) * 6848.0 / 105.0
-    )
-    c6LogT = 6848.0 / 105.0
-
-    c5T = 13.0 * Pi * eta / 3.0 - 7729.0 * Pi / 252.0
-
-    c4T = 3058673.0 / 508032.0 + eta * (5429.0 / 504.0 + eta * 617.0 / 72.0)
-    c3T = -32.0 * Pi / 5.0
-    c2T = 743.0 / 252.0 + eta * 11.0 / 3.0
-    c0T = 5.0 * m * MTSUN_SI / (256.0 * eta)
-
[…]

### 2025-06-21 gwsnr/numba/__init__.py

@@ -1,0 +1,2 @@
+from .njit_functions import *
+from .njit_interpolators import *

### 2025-06-21 gwsnr/numba/njit_functions.py

@@ -4,7 +4,7 @@ Helper functions for gwsnr. All functions are njit compiled.
 """
 
 import numpy as np
-from numba import njit, jit
+from numba import njit
 
 Gamma = 0.5772156649015329
 Pi = np.pi
@@ -113,6 +113,7 @@ def einsum1(m,n):
     ans[2,1] = m[2]*n[1]
     ans[2,2] = m[2]*n[2]
     return ans
+
 @njit
 def einsum2(m,n):
     """
@@ -300,245 +301,6 @@ def noise_weighted_inner_product(
 
     nwip_arr = np.conj(signal1) * signal2 / psd
     return 4 / duration * np.sum(nwip_arr)
-
-@njit
-def get_interpolated_snr(mass_1, mass_2, luminosity_distance, theta_jn, psi, geocent_time, ra, dec, detector_tensor, snr_partialscaled, ratio_arr, mtot_arr):
-    """
-    Function to calculate the interpolated snr for a given set of parameters
-
-    Parameters
-    ----------
-    mass_1 : `numpy.ndarray`
-        Mass of the first body in solar masses.
-    mass_2 : `numpy.ndarray`
-        Mass of the second body in solar masses.
-    luminosity_distance : `float`
-        Luminosity distance to the source in Mpc.
-    theta_jn : `numpy.ndarray`
-        Angle between the total angular momentum and the line of sight to the source in radians.
-    psi : `numpy.ndarray`
-        Polarization angle of the source.
-    geocent_time : `numpy.ndarray`
-        GPS time of the source.
-    ra : ``numpy.ndarray`
-        Right ascension of the source in radians.
-    dec : `numpy.ndarray`
-        Declination of the source in radians.
-    detector_tensor : array-like
-        Detector tensor for the detector (3x3 matrix)
-    snr_partialscaled : `numpy.ndarray`
-        Array of snr_partialscaled coefficients for the detector.
-    ratio_arr : `numpy.ndarray`
-        Array of mass ratio values for the snr_partialscaled coefficients.
-    mtot_arr : `numpy.ndarray`
-        Array of total mass values for the snr_partialscaled coefficients.
-    
-    Returns
-    -------
-    snr : `float`
[…]

### 2025-06-21 gwsnr/numba/njit_interpolators.py

@@ -1,0 +1,469 @@
+import numpy as np
+from numba import njit, prange
+from .njit_functions import antenna_response_array
+
+@njit
+def get_interpolated_snr(mass_1, mass_2, luminosity_distance, theta_jn, psi, geocent_time, ra, dec, detector_tensor, snr_partialscaled, ratio_arr, mtot_arr):
+    """
+    Function to calculate the interpolated snr for a given set of parameters
+
+    Parameters
+    ----------
+    mass_1 : `numpy.ndarray`
+        Mass of the first body in solar masses.
+    mass_2 : `numpy.ndarray`
+        Mass of the second body in solar masses.
+    luminosity_distance : `float`
+        Luminosity distance to the source in Mpc.
+    theta_jn : `numpy.ndarray`
+        Angle between the total angular momentum and the line of sight to the source in radians.
+    psi : `numpy.ndarray`
+        Polarization angle of the source.
+    geocent_time : `numpy.ndarray`
+        GPS time of the source.
+    ra : ``numpy.ndarray`
+        Right ascension of the source in radians.
+    dec : `numpy.ndarray`
+        Declination of the source in radians.
+    detector_tensor : array-like
+        Detector tensor for the detector (3x3 matrix)
+    snr_partialscaled : `numpy.ndarray`
+        Array of snr_partialscaled coefficients for the detector.
+    ratio_arr : `numpy.ndarray`
+        Array of mass ratio values for the snr_partialscaled coefficients.
+    mtot_arr : `numpy.ndarray`
+        Array of total mass values for the snr_partialscaled coefficients.
+    
+    Returns
+    -------
+    snr : `float`
+        snr of the detector.
+    """
+
+    size = len(mass_1)
+    len_ = len(detector_tensor)
+    mtot = mass_1 + mass_2
+    ratio = mass_2 / mass_1
+    # get array of antenna response
+    Fp, Fc = antenna_response_array(ra, dec, geocent_time, psi, detector_tensor)
+
[…]

### 2025-06-21 gwsnr/numba/njit_interpolators_old.py

@@ -1,0 +1,4 @@
+import numpy as np
+from numba import njit
+from .njit_functions import antenna_response_array
+

### 2025-06-21 gwsnr/ripple/__init__.py

@@ -1,0 +1,1 @@
+from .ripple_class import *

### 2025-06-21 gwsnr/ripple/ripple_class.py

@@ -3,65 +3,18 @@ import jax.numpy as jnp
 from ripple import ms_to_Mc_eta
 from jax import vmap
 from jax import jit
-from .njit_functions import noise_weighted_inner_product
-from .jaxjit_functions import findchirp_chirptime_jax
-import bilby
+from ..jax import findchirp_chirptime_jax
+import multiprocessing as mp
 from multiprocessing import Pool
 from tqdm import tqdm
 
-from .multiprocessing_routine import noise_weighted_inner_prod_ripple
+from ..utils import noise_weighted_inner_prod_ripple
 
 class RippleInnerProduct:
     """
     Class to compute the noise weighted inner product for a given waveform and PSD
-
-    Parameters
-    ----------
-    waveform_name: `str`
-        The name of the waveform to use. Ripple supported waveforms are as follows, along with corresponding required arguments: 
-        IMRPhenomXAS (aligned spin): theta = ['Mchirp', 'eta', 'a_1', 'a_2', 'luminosity_distance', 'tc', 'phase', 'theta_jn']
-        IMRPhenomD (aligned spin): theta = ['Mchirp', 'eta', 'a_1', 'a_2', 'luminosity_distance', 'tc', 'phase', 'theta_jn']
-        IMRPhenomPv2 (Still finalizing sampling checks): not known
-        TaylorF2 with tidal effects : ['Mchirp', 'eta', 'a_1', 'a_2', 'lambda_1', 'lambda_2','luminosity_distance', 'tc', 'phase', 'theta_jn']
-            lambda_1: Dimensionless tidal deformability of the primary object [between 0 and 5000]
-            lambda_2: Dimensionless tidal deformability of the secondary object [between 0 and 5000]
-        IMRPhenomD_NRTidalv2, verified for the low spin regime (a_1, a_2 < 0.05), further testing is required for higher spins: ['Mchirp', 'eta', 'a_1', 'a_2', 'lambda_1', 'lambda_2','luminosity_distance', 'tc', 'phase', 'theta_jn']
-        Note: keep tc=0.0s
-    minimum_frequency: `float`
-        Default is 20.0 Hz
-    sampling_frequency: `float`
-        Default is 2048.0 Hz
-    reference_frequency: `float`
-        Default is minimum_frequency
-
-    Waveform argument descriptions:\n
-    +--------------------+--------------+--------------------------------------+
-    | Parameter          | Units        | Description                          |
-    +====================+==============+======================================+
-    | Mchirp             | Solar Mass   | Chirp mass                           |
[…]

### 2025-06-21 gwsnr/ripple/ripple_class_dev.py

@@ -1,0 +1,179 @@
+import numpy as np
+import jax.numpy as jnp
+from ripple import ms_to_Mc_eta
+from jax import vmap
+from jax import jit
+from ..jax import findchirp_chirptime_jax
+from multiprocessing import Pool
+from tqdm import tqdm
+
+from ..utils import noise_weighted_inner_prod_ripple
+
+class RippleInnerProduct:
+    """
+    Class to compute the noise weighted inner product for a given waveform and PSD
+    """
+
+    def __init__(self, waveform_name, minimum_frequency=20.0, sampling_frequency=2048.0, reference_frequency=None):
+        
+        self.f_u = sampling_frequency/2
+        self.f_ref = reference_frequency if reference_frequency is not None else minimum_frequency
+        self.f_l = minimum_frequency
+        self.arg_list = self.arg_selection(waveform_name)
+        self.gen_hphc = jit(self.select_waveform(waveform_name))
+        self.vmap_waveform = vmap(self.gen_hphc)
+        self.vmap_findchirp_chirptime = vmap(findchirp_chirptime_jax)
+
+    def arg_selection(self, waveform_name):
+        """
+        Returns the list of arguments required for the chosen waveform.
+
+        Parameters
+        ----------
+        waveform_name: `str`
+            The name of the waveform to use. Ripple supported waveforms only.
+        
+        Returns
+        -------
+        list: List of arguments required for the chosen waveform.
+        """
+
+        supported_waveforms = ['IMRPhenomXAS', 'IMRPhenomD', 'TaylorF2', 'IMRPhenomD_NRTidalv2']
+
+        if waveform_name == 'IMRPhenomXAS':
+            return ['Mchirp', 'eta', 'a_1', 'a_2', 'luminosity_distance', 'tc', 'phase', 'theta_jn']
+        elif waveform_name == 'IMRPhenomD':
+            return ['Mchirp', 'eta', 'a_1', 'a_2', 'luminosity_distance', 'tc', 'phase', 'theta_jn']
+        elif waveform_name == 'TaylorF2':
+            return ['Mchirp', 'eta', 'a_1', 'a_2', 'lambda_1', 'lambda_2','luminosity_distance', 'tc', 'phase', 'theta_jn']
+        elif waveform_name == 'IMRPhenomD_NRTidalv2':
+            return ['Mchirp', 'eta', 'a_1', 'a_2', 'lambda_1', 'lambda_2','luminosity_distance', 'tc', 'phase', 'theta_jn']
+        else:
[…]

### 2025-06-21 gwsnr/utils/__init__.py

@@ -1,0 +1,2 @@
+from .utils import *
+from .multiprocessing_routine import *

### 2025-06-21 gwsnr/utils/multiprocessing_routine.py

@@ -6,7 +6,7 @@ Helper functions for multiprocessing in snr generation
 import numpy as np
 import bilby
 
-from .njit_functions import noise_weighted_inner_product
+from ..numba import noise_weighted_inner_product
 
 
 def noise_weighted_inner_prod(params):

### 2025-06-21 setup.py

@@ -1,45 +1,84 @@
 #!/usr/bin/env python
 from setuptools import setup, find_packages
 import sys
-# read the contents of your README file
 from pathlib import Path
+
+# read the contents of your README file
 this_directory = Path(__file__).parent
 long_description = (this_directory / "README.md").read_text()
 
-# check that python version is 3.7 or above
+# check that python version is 3.10 or above
 python_version = sys.version_info
 if python_version < (3, 10):
     sys.exit("Python < 3.10 is not supported, aborting setup")
 
-#!/usr/bin/env python
-from setuptools import setup, find_packages
-setup(name='gwsnr',
-      version='0.3.3',
-      description='gwsnr: A Python Package for Efficient SNR Calculation of Gravitational Waves',
-      author='Hemantakumar Phurailatpam',
-      license="MIT",
-      author_email='hemantaphurailatpam@gmail.com',
-      url='https://github.com/hemantaph/gwsnr',
-      packages=find_packages(),
-      package_data={
-        'gwsnr': ['ann/*.json', 'ann/*.pkl', 'ann/*.h5'],
-      },
-      install_requires=[
-        "setuptools>=65.5.0",
-        "matplotlib>=3.4.2",
-        "numpy>=1.18",
-        "bilby>=1.0.2",
-        "pycbc>=2.0.4",
-        "scipy<1.14.0",
-        "tqdm>=4.64.0",
-        "gwpy>=2.1.5",
-        "h5py>=3.11.0,<3.12.0",
-        "numba>=0.57.1,<0.58.0",
-        "numba>=0.57.1",
-        "ml-dtypes==0.3.1", # new
-        "tensorflow>=2.17.0,<2.18.0",
-        "scikit-learn==1.5.0",
-        "numexpr>=2.8.4",
-        "ripplegw",
-      ]
-     )
+# Read requirements from requirements.txt
+def parse_requirements(filename):
+    with open(filename, 'r') as f:
+        lines = f.read().splitlines()
+    return [line.strip() for line in lines if line.strip() and not line.startswith('#')]
+
+requirements = parse_requirements("requirements.txt")
+
+setup(
+    name='gwsnr',
+    version='0.3.3',
+    description='gwsnr: A Python Package for Efficient SNR Calculation of Gravitational Waves',
+    long_description=long_description,
+    long_description_content_type='text/markdown',
[…]

### 2025-06-21 arxiv/paper_old.tex
mac

--- 2024-11-24 arxiv/paper.tex
@@
 
-        \author[1]{Phurailatpam Hemantakumar}
+        \author[1]{Hemantakumar Phurailatpam}
           \author[1]{Otto Akseli HANNUKSELA}
@@
 conditions. Other similar efforts with ANN models are detailed in
-Chapman-Bird et al. (2023), Gerosa et al. (2020) etc.
+Chapman-Bird et al. (2023), Gerosa et al. (2020), Callister et al.
+(2024) etc.
+
+In addition to providing trained ANN models for specific configurations,
+\emph{\texttt{gwsnr}} offers users the flexibility to develop and train
+custom models tailored to their unique requirements. This adaptability
+allows for optimization based on variations in detector sensitivity,
+gravitational wave properties, and other research-specific factors,
+ensuring maximum model effectiveness across different scenarios.
 
@@
 
+\bibitem[\citeproctext]{ref-Callister2024}
+Callister, Thomas A. et al. 2024. {``Neural Network Emulator of the
+Advanced LIGO and Advanced Virgo Selection Function.''} \emph{Physical
+Review D} 110 (12). \url{https://doi.org/10.1103/physrevd.110.123041}.
+
 \bibitem[\citeproctext]{ref-ChapmanBird2023}

### 2025-06-21 arxiv/paper.tex
mac

--- 2024-11-09 arxiv/paper.tex
@@
 \hypersetup{unicode=true,
-            pdftitle={gwsnr: A Python Package for Efficient SNR Calculation of GWs},
+            pdftitle={gwsnr: A python package for efficient signal-to-noise calculation of gravitational-waves},
             pdfborder={0 0 0},
@@
 
-\title{\texttt{gwsnr}: A Python Package for Efficient SNR Calculation of
-GWs}
+\title{\texttt{gwsnr}: A python package for efficient signal-to-noise
+calculation of gravitational-waves}
 
-        \author[1]{Phurailatpam Hemantakumar}
+        \author[1]{Hemantakumar Phurailatpam}
           \author[1]{Otto Akseli HANNUKSELA}
@@
 theory of General Relativity, have revolutionized astrophysics since
-their first detection in 2015 (Abbott, B. P. et al. (2016a)). These
-waves are emitted by cataclysmic events like the merging of binary black
-holes (BBHs), binary neutron stars (BNSs) and BH-NS pairs, providing a
-unique window into the cosmos. A critical aspect of GW analysis is the
-Signal-to-Noise Ratio (SNR). SNR quantifies the strength of a GW signal
-relative to the background noise in a detector, like LIGO (The LIGO
-Scientific Collaboration et al. (2015), Abbott et al. (2020), Buikema et
-al. (2020)), Virgo (F. Acernese et al. (2014), F. Acernese et al.
-(2019)) or KAGRA (Akutsu et al. (2020), Aso et al. (2013)). This ratio
-is pivotal in confirming the detection of GWs and extracting
-astrophysical information from them (Abbott, B. P. et al. (2016b)).
-However, specific scenarios in GW research, particularly in simulations
-of detectable GW events (Abbott et al. (2016)) and in hierarchical
-Bayesian analysis (Thrane and Talbot (2019)) where selection effects are
-considered, demand extensive and efficient computation of SNR. This
-requirement presents a significant challenge, as conventional
-computational approaches, such as noise-weighted inner product, are
-typically time-consuming and impractical for such specialized and
-large-scale analyses (Taylor and Gerosa (2018), Gerosa et al. (2020)).
+their first detection in 2015 (Abbott, B. P. et al. (2016a), B.  P.
+Abbott et al. (2016)). These waves are emitted by cataclysmic events
+like the merging of binary black holes (BBHs), binary neutron stars
+(BNSs) and BH-NS pairs, providing a unique window into the cosmos. A
+critical aspect of GW analysis is the Signal-to-Noise Ratio (SNR). SNR
+quantifies the strength of a GW signal relative to the background noise
+in a detector, like LIGO (The LIGO Scientific Collaboration et al.
+(2015), B. P. Abbott et al. (2020), Buikema et al. (2020)), Virgo (F.
+Acernese et al. (2014), F. Acernese et al. (2019)) or KAGRA (Akutsu et
+al. (2020), Aso et al. (2013)). This ratio is pivotal in confirming the
+detection of GWs and extracting astrophysical information from them
+(Abbott, B. P. et al. (2016b)). However, specific scenarios in GW
+research, particularly in simulations of detectable GW events (B. P.
+Abbott et al. (2016)) and in hierarchical Bayesian analysis (Thrane and
+Talbot (2019)) where selection effects are considered, demand extensive
+and efficient computation of SNR. This requirement presents a
+significant challenge, as conventional computational approaches, such as
+noise-weighted inner product, are typically time-consuming and
+impractical for such specialized and large-scale analyses (Taylor and
+Gerosa (2018), Gerosa et al. (2020)).
 
@@
 The \emph{\texttt{gwsnr}} Python package addresses the need for
-efficient SNR computation in GW research. It innovatively streamlines
-SNR calculations, enhancing accuracy and efficiency with several
-advanced techniques. Firstly, it utilizes an innovative interpolation
+efficient SNR computation in GW research. It provides a flexible and
+user-friendly interface, allowing users to combine various detector
+noise models, waveform models, detector configurations, and signal
+parameters. \emph{\texttt{gwsnr}} enhances SNR calculations through
+several key features. Firstly, it utilizes an innovative interpolation
 method, employing a partial-scaling approach for accurately
-interpolating the SNR of GWs from spin-less binary systems wrt to their
-mass parameters. Secondly, the package features a noise-weighted inner
-product method, similar to that in the \emph{\texttt{bilby}} package
-(Ashton, Gregory et al. (2022)), but enhanced with multiprocessing
-capabilities. This integration allows for the parallel processing of
-complex calculations, thereby expediting the SNR computation. Thirdly, a
-trained Artificial Neural Network (ANN) model is incorporated for rapid
-`probability of detection' (Pdet) estimation for BBH systems with spin
-precession. Lastly, \emph{\texttt{gwsnr}} leverages the
-\emph{\texttt{numba}}'s Just-In-Time (njit) compiler (Lam, Pitrou, and
-Seibert (2022)), which optimizes performance by compiling Python code
-into machine code at runtime, drastically reducing execution times.
-Beyond these technical merits, \emph{\texttt{gwsnr}} stands out for its
-user-friendly features and seamless integration with other related
-software packages, making it not just a powerful tool but also an
-accessible one for researchers. These attributes position
-\emph{\texttt{gwsnr}} as an invaluable asset in GW data analysis,
-particularly in simulations of detectable compact binary mergers,
-determining rates of GW events, related to both lensed and un-lensed
-events (Phurailatpam et al. (2024), Ng et al. (2024)), and in the
+interpolating the SNR of GWs from spin-less and spin-aligned binary
+systems. Secondly, the package features a noise-weighted inner product
+method, similar to that in the \emph{\texttt{bilby}} package (Ashton et
+al. (2019), Ashton, Gregory et al. (2022)), but enhanced with
+multiprocessing capabilities. This parallel processing is crucial for
+handling large datasets and computationally intensive analyses. Thirdly,
+a trained Artificial Neural Network (ANN) model is incorporated for
+rapid `probability of detection' (Pdet) estimation for BBH systems with
+spin precession. Lastly, \emph{\texttt{gwsnr}} leverages
+\emph{\texttt{numpy}} (NumPy Community (2022)) vectorization, and
+\emph{\texttt{numba}}'s (Lam, Pitrou, and Seibert (2022)) and
+\emph{\texttt{JAX}}'s (James Bradbury and others (2018)) Just-In-Time
+compiler (\texttt{numbba.njit} and \texttt{jax.jit}), which optimizes
+performance by compiling Python code into machine code at runtime,
+drastically reducing execution times. This combination of advanced
+techniques and user-friendly design makes gwsnr a valuable tool for GW
+data analysis, particularly in simulating detectable compact binary
+mergers, determining rates of both lensed and unlensed GW events (as
+demonstrated by its use in the \emph{\texttt{ler}} package; Phurailatpam
+et al. (2024), Ng et al. (2024), More and Phurailatpam (2025), Janquart
+et al. (2023), R. Abbott et al. (2021), Collaboration et al. (2023),
+Wierda et al. (2021), Wempe et al. (2022)), and will help in the
 analysis of selection effects within hierarchical Bayesian frameworks
-(Thrane and Talbot (2019)). The package thus represents a significant
-step forward in aiding GW research, enabling more precise and efficient
-exploration of the universe through GW observations and simulations.
-Additionally, \emph{\texttt{gwsnr}} is instrumental in the
-\emph{\texttt{ler}} (Phurailatpam et al. (2024)) package for calculating
-detectable rates of both lensed and unlensed GW events, showcasing its
-utility in advanced GW studies.
+(Thrane and Talbot (2019)).
 
@@
 
-\paragraph{Modified FINDCHIRP Method: Partial Scaling
-Approach}\label{modified-findchirp-method-partial-scaling-approach}
+The \texttt{gwsnr} package provides two efficient methods for computing
+the optimal SNR in GW data analysis: the Noise-Weighted Inner Product
+Method with Multiprocessing and the Partial Scaling Interpolation
+Method. In addition, there are two approaches for estimating
+\(P_{\rm det}\) for precessing systems: ANN-based \(P_{\rm det}\)
+Estimation and the Partial Scaling Interpolation Method with SNR
+recalculation. Extensive details of these methods can be found in the
+package documentation (Phurailatpam and Hannuksela (2025)).
 
-The \emph{\texttt{gwsnr}} package introduces the Partial Scaling method
-for SNR calculations in spin-less binary systems. This method, rooted in
-the FINDCHIRP algorithm (Allen et al. (2012)), focuses on non-spinning
-inspiral-merger-ringdown (IMR) waveforms, in lalsimulation library (LIGO
-Scientific Collaboration, Virgo Collaboration, and KAGRA Collaboration
-(2018)), and particularly interpolates the Partial scaled SNR
-(\(\rho_{1/2}\)) based on mass parameters (\(M_{tot},q\)).
-
-\begin{itemize}
-\item
-  \textbf{Interpolation Method}: Utilizes a 2D cubic spline technique
-  (njit-ted) for the `partialsnr' segment.
-\item
-  \textbf{Equations}:
-
-  \begin{itemize}
-  \item
-    For a simple inspiral waveform, the optimal SNR is given by,
-    \[\rho = F(D_l,\mathcal{M},\iota,\psi,\alpha, \delta) \sqrt{ 4\int_0^{f_{ISCO}} \frac{f^{-7/3}}{S_n(f)}df }\]
-  \item
-    \(F\) is defined as a function of luminosity distance (\(D_l\)),
-    chirp mass (\(\mathcal{M}\)), inclination angle (\(\iota\)),
-    polarization angles (\(\psi\)), right ascension (\(\alpha\)), and
-    declination (\(\delta\)), refer to Eqn(D1) of Allen et al. (2012).
-    \(f\) is the frequency, \(f_{ISCO}\) is the last stable orbit
-    frequency and \(S_n(f)\) is the detector's noise curve or power
-    spectral density (psd).
-  \item
-    Then, partial scaled SNR:
-    \(\rho_{1/2} = \sqrt{ 4\int_0^\infty \frac{f^{-7/3}}{S_n(f)}df } \approx \sqrt{ 4\int_0^{f_{ISCO}} \frac{f^{-7/3}}{S_n(f)}df }\)
-  \item
-    For an spinless frequency-domain IMR waveform with optimal SNR equal
-    to \(\rho\):
-    \(\rho_{1/2} = \rho\,/\, F(D_l,\mathcal{M},\iota,\psi,\alpha, \delta)\)
-  \item
-    \(\rho_{1/2}\) is considered a function of \(M_{tot}\) and \(q\).
-  \end{itemize}
-\end{itemize}
-
-\paragraph{Noise-Weighted Inner Product Method with
+\subsubsection{Noise-Weighted Inner Product Method with
 Multiprocessing}\label{noise-weighted-inner-product-method-with-multiprocessing}
 
-Designed for SNR calculations in systems characterized by frequency
-domain waveforms in \emph{\texttt{lalsimulation}} (LIGO Scientific
-Collaboration, Virgo Collaboration, and KAGRA Collaboration (2018)),
-including spin-precessing binary systems.
+The noise-weighted inner product is a robust and widely used technique,
+suitable for any frequency-domain gravitational waveform, including
+complex models with spin precession and higher-order harmonics available
+in \texttt{lalsimulation} (LIGO Scientific Collaboration, Virgo
+Collaboration, and KAGRA Collaboration (2018)). Following (Allen et al.
+(2012)), the inner product between two frequency-domain signals,
+\(\tilde{a}(f)\) and \(\tilde{b}(f)\), is defined as:
 
-\begin{itemize}
-\item
-  \textbf{Methodology}: Combines waveform generation (multi-process),
-  antenna pattern calculation (njit-ted), and noise-weighted inner
-  product computation (njit-ted).
-\item
-  \textbf{Equations}:
+\[
+\left< a | b \right> = 4 \Re \int_{f_{\min}}^{f_{\max}} \frac{\tilde{a}(f)\tilde{b}^*(f)}{S_n(f)} df
+\]
 
-  \begin{itemize}
-  \item
-    Inner product:
-    \(\left< a | b \right> = 4 \int_{f_{min}}^{f_{max}} \frac{\tilde{a}(f)\tilde{b}^*(f)}{S_n(f)} df\)
-  \item
-    Optimal SNR:
-    \(\rho = \sqrt{ F_+^2 \left< \tilde{h}_+ | \tilde{h}_+ \right> + F_{\times}^2 \left< \tilde{h}_{\times} | \tilde{h}_{\times} \right> }\),
-    for orthogonal \(h_+\) and \(h_{\times}\).
-  \item
-    \(h_{+\times}\) are frequency domain waveform polarizations, and
-    \(F_{+\times}\) are antenna patterns.
-  \end{itemize}
-\end{itemize}
+Here, \(S_n(f)\) is the one-sided power spectral density of the detector
+noise, and \((f_{\min}, f_{\max})\) is the analysis frequency band. The
+optimal SNR \(\rho\), is the norm of the inner-product for the given
+signal \(h\) : \(\rho = \sqrt{\langle h | h \rangle}\). For a
+gravitational wave signal composed of plus (\(h_+\)) and cross
+(\(h_\times\)) polarizations, and assuming orthogonality between them,
+the SNR can be expressed in terms of the detector's antenna patterns,
+\(F_+\) and \(F_\times\):
 
-These formulations highlight \emph{\texttt{gwsnr}}'s capability to
-efficiently process diverse GW signals, enhancing data analysis accuracy
-and efficiency.
+\[
+\rho = \sqrt{ F_+^2 \left< \tilde{h}_+ | \tilde{h}_+ \right> + F_{\times}^2 \left< \tilde{h}_{\times} | \tilde{h}_{\times} \right> }
+\]
 
-\paragraph{Artificial Neural Network (ANN) Model for Pdet
-Estimation}\label{artificial-neural-network-ann-model-for-pdet-estimation}
+While this approach is versatile, it can be computationally intensive,
+with waveform generation representing the primary bottleneck. The
+\texttt{gwsnr} package addresses this challenge by parallelizing
+waveform generation across multiple CPU cores and accelerating the
+antenna pattern and inner product calculations using \texttt{numba.njit}
+compilation. Additionally, \texttt{gwsnr} provides optional support for
+JAX-based waveform generation and acceleration via the \texttt{ripple}
+waveform library (Edwards et al. 2024), utilizing \texttt{jax.jit} for
+just-in-time compilation and \texttt{jax.vmap} for efficient batched
+operations.
 
-The \emph{\texttt{gwsnr}} package now incorporates an artificial neural
-network (ANN) model, developed using \emph{\texttt{TensorFlow}} (Abadi
-et al. (2015)) and \emph{\texttt{sklearn}} (Pedregosa et al. (2011)), to
-rapidly estimate the Pdet in binary black hole (BBH) systems using the
+\subsubsection{Partial Scaling Interpolation
+Method}\label{partial-scaling-interpolation-method}
+
+For non-spinning or aligned-spin binary systems restricted to the
+dominant harmonic mode, \texttt{gwsnr} implements a highly efficient
+interpolation-based technique called the Partial Scaling method. This
+approach, adapted from the FINDCHIRP algorithm (Allen et al. (2012)),
+decouples the computationally expensive parts of the SNR calculation
+from the extrinsic source parameters. It achieves this by defining a
+``partial-scaled SNR'' \(\rho_{1/2}\), which isolates the dependence on
+the intrinsic parameters (masses and spins). For a given full IMR
+waveform SNR, \(\rho_{\text{full}}\), the partial SNR is defined as:
+
+\[
+\rho_{1/2} = \left(\frac{D_\mathrm{eff}}{1~\mathrm{Mpc}}\right) \left(\frac{\mathcal{M}}{M_\odot}\right)^{-5/6} \times \rho_{\text{full}}
+\]
+
+Here, \(\mathcal{M}\) is the chirp mass and \(D_{\text{eff}}\) is the
+effective distance, which encapsulates the luminosity distance, sky
+location, and detector orientation wrt the binary. Since \(\rho_{1/2}\)
+depends only on the intrinsic properties of the binary, its value can be
+pre-computed on a grid and stored. For non-spinning systems, this is a
+two-dimensional grid of total mass (\(M\)) and mass ratio (\(q\)), while
+for aligned-spin systems, it is a four-dimensional grid that also
+includes the two spin magnitudes. To find the SNR for a new binary,
+\texttt{gwsnr} performs a rapid cubic spline interpolation on the
+pre-computed grid to find the corresponding \(\rho_{1/2}\) value. The
+final SNR is then recovered almost instantaneously by applying the
+scaling transformation:
+
+\[
+\rho = \rho_{1/2} \times \left(\frac{\mathcal{M}}{M_\odot}\right)^{5/6} \times \left(\frac{1~\mathrm{Mpc}}{D_\mathrm{eff}}\right)
+\]
+
+This procedure transforms a computationally intensive integration into a
+simple, JIT-compiled table lookup and multiplication, enabling massive
+performance gains for large-scale population studies.
+
+\subsubsection{ANN-based Pdet
+Estimation}\label{ann-based-pdet-estimation}
+
+The \texttt{gwsnr} package now incorporates an artificial neural network
+(ANN) model, developed using TensorFlow (Abadi et al. (2015)) and
+scikit-learn (Pedregosa et al. (2011)), to rapidly estimate
+\(P_{\rm det}\) in binary black hole (BBH) systems using the
 IMRPhenomXPHM waveform approximant. This complex IMR waveform model
@@
 calculations are not critical, providing a quick and effective means of
-estimating Pdet. This value indicates detectability under Gaussian noise
-by determining if the SNR exceeds a certain threshold. Trained on a
-large dataset from the \emph{\texttt{ler}} package, the ANN model uses
-`partial scaled SNR' values as a primary input, reducing input
-dimensionality from 15 to 5 and enhancing accuracy. This approach offers
-a practical solution for assessing detectability under specified
-conditions. Other similar efforts with ANN models are detailed in
-Chapman-Bird et al. (2023), Gerosa et al. (2020) etc.
+estimating \(P_{\rm det}\). This value indicates detectability under
+Gaussian noise by determining if the SNR exceeds a certain threshold
+(e.g., \(\rho_{\rm th}=8\)). Trained on a large dataset from the
+\texttt{ler} package, the ANN model uses `partial scaled SNR' values as
+a primary input, reducing input dimensionality from 15 to 5 and
+enhancing accuracy. This approach offers a practical solution for
+assessing detectability under specified conditions. Other similar
+efforts with ANN models are detailed in (Chapman-Bird et al. (2023),
+Gerosa et al. (2020), Callister et al. (2024)).
+
+In addition to providing trained ANN models for specific configurations,
+\texttt{gwsnr} offers users the flexibility to develop and train custom
+models tailored to their unique requirements. This adaptability allows
+for optimization based on variations in detector sensitivity,
+gravitational-wave properties, and other research-specific factors,
+ensuring maximum model effectiveness across different scenarios.
+
+\subsubsection{Partial Scaling Interpolation Method with SNR
+Recalculation for Pdet
+Estimation}\label{partial-scaling-interpolation-method-with-snr-recalculation-for-pdet-estimation}
+
+While the Partial Scaling method is highly efficient for aligned-spin
+systems, its utility can be further enhanced by recalculating the SNR
+for precessing systems within a predefined small range of generated
+SNRs. This is done by first obtaining optimal SNRs with the Partial
+Scaling method, selecting the SNRs near \(\rho_{\rm th}\), and then
+recalculating the SNRs for these systems using the Noise-Weighted Inner
+Product Method. This approach allows us to leverage the speed of the
+Partial Scaling method while ensuring accurate SNR values for systems
+close to the detection threshold. The recalculated SNRs can then be used
+to estimate \(P_{\rm det}\), providing a balance between computational
+efficiency and accuracy.
 
@@
 
-\section*{References}\label{references}
-\addcontentsline{toc}{section}{References}
-
 \phantomsection\label{refs}
 \begin{CSLReferences}{1}{0}
-\bibitem[\citeproctext]{ref-tensorflow2015}
+\bibitem[\citeproctext]{ref-tensorflow:2015}
 Abadi, Martín, Ashish Agarwal, Paul Barham, Eugene Brevdo, Zhifeng Chen,
@@
 
-\bibitem[\citeproctext]{ref-Abbott2020}
+\bibitem[\citeproctext]{ref-Abbott:2016:pe}
+Abbott, B. P., R. Abbott, T. D. Abbott, M. R. Abernathy, F. Acernese, K.
+Ackley, C. Adams, et al. 2016. {``Properties of the Binary Black Hole
+Merger GW150914.''} \emph{Physical Review Letters} 116 (24).
+\url{https://doi.org/10.1103/physrevlett.116.241102}.
+
+\bibitem[\citeproctext]{ref-Abbott:2020}
 Abbott, B. P., R. Abbott, T. D. Abbott, S. Abraham, F. Acernese, K.
@@
 
-\bibitem[\citeproctext]{ref-virgo:2019}
+\bibitem[\citeproctext]{ref-Abbott:2021}
+Abbott, R., T. D. Abbott, S. Abraham, F. Acernese, K. Ackley, A. Adams,
+C. Adams, et al. 2021. {``Search for Lensing Signatures in the
+Gravitational-Wave Observations from the First Half of LIGO--Virgo's
+Third Observing Run.''} \emph{The Astrophysical Journal} 923 (1): 14.
+\url{https://doi.org/10.3847/1538-4357/ac23db}.
+
+\bibitem[\citeproctext]{ref-VIRGO:2019}
 Acernese, F., M. Agathos, L. Aiello, A. Allocca, A. Amato, S. Ansoldi,
@@
 
-\bibitem[\citeproctext]{ref-VIRGO2015}
+\bibitem[\citeproctext]{ref-VIRGO:2015}
 Acernese, F, M Agathos, K Agatsuma, D Aisa, N Allemandou, A Allocca, J
@@
 
-\bibitem[\citeproctext]{ref-akutsu2020overviewkagradetectordesign}
+\bibitem[\citeproctext]{ref-Akutsu:2020}
 Akutsu, T., M. Ando, K. Arai, Y. Arai, S. Araki, A. Araya, N. Aritomi,
@@
 
-\bibitem[\citeproctext]{ref-bilby}
+\bibitem[\citeproctext]{ref-Ashton:2022}
 Ashton, Gregory, Sylvia Biscoveanu, Neil Cornish, Isaac Dal Canto,
@@
 
-\bibitem[\citeproctext]{ref-PhysRevD:88:043007}
+\bibitem[\citeproctext]{ref-Ashton:2019}
+Ashton, Gregory, Moritz Hübner, Paul D. Lasky, Colm Talbot, Kendall
+Ackley, Sylvia Biscoveanu, Qi Chu, et al. 2019. {``Bilby: A
+User-Friendly Bayesian Inference Library for Gravitational-Wave
+Astronomy.''} \emph{The Astrophysical Journal Supplement Series} 241
+(2): 27. \url{https://doi.org/10.3847/1538-4365/ab06fc}.
+
+\bibitem[\citeproctext]{ref-Aso:2013}
 Aso, Yoichi, Yuta Michimura, Kentaro Somiya, Masaki Ando, Osamu
@@
 
-\bibitem[\citeproctext]{ref-PhysRevD.102.062003}
+\bibitem[\citeproctext]{ref-Buikema:2020}
 Buikema, A., C. Cahillane, G. L. Mansell, C. D. Blair, R. Abbott, C.
@@
 
-\bibitem[\citeproctext]{ref-ChapmanBird2023}
+\bibitem[\citeproctext]{ref-Callister:2024}
+Callister, Thomas A. et al. 2024. {``Neural Network Emulator of the
+Advanced LIGO and Advanced Virgo Selection Function.''} \emph{Physical
+Review D} 110 (12). \url{https://doi.org/10.1103/physrevd.110.123041}.
+
+\bibitem[\citeproctext]{ref-ChapmanBird:2023}
 Chapman-Bird, Christian E A et al. 2023. {``Rapid Determination of LISA
@@
 6043--54. \url{https://doi.org/10.1093/mnras/stad1397}.
+
+\bibitem[\citeproctext]{ref-ligolensing:2023}
+Collaboration, The LIGO Scientific, the Virgo Collaboration, the KAGRA
+Collaboration, R. Abbott, H. Abe, F. Acernese, K. Ackley, et al. 2023.
+{``Search for Gravitational-Lensing Signatures in the Full Third
+Observing Run of the LIGO-Virgo Network.''}
+\url{https://arxiv.org/abs/2304.08393}.
+
+\bibitem[\citeproctext]{ref-Edwards:2023}
+Edwards, Thomas D. P., Kaze W. K. Wong, Kelvin K. H. Lam, Adam Coogan,
+Daniel Foreman-Mackey, Maximiliano Isi, and Aaron Zimmerman. 2024.
+{``{Differentiable and hardware-accelerated waveforms for gravitational
+wave data analysis}.''} \emph{Phys. Rev. D} 110 (6): 064028.
+\url{https://doi.org/10.1103/PhysRevD.110.064028}.
 
@@
 
-\bibitem[\citeproctext]{ref-numba}
+\bibitem[\citeproctext]{ref-jax:2018}
+James Bradbury, Peter Hawkins, Roy Frostig, and Various others. 2018.
+{``JAX: Composable Transformations of Python+NumPy Programs.''} GitHub.
+\url{https://github.com/google/jax}.
+
+\bibitem[\citeproctext]{ref-Janquart:2023}
+Janquart, J, M Wright, S Goyal, J C L Chan, A Ganguly, Á Garrón, D
+Keitel, et al. 2023. {``{Follow-up analyses to the O3 LIGO--Virgo--KAGRA
+lensing searches}.''} \emph{Monthly Notices of the Royal Astronomical
+Society} 526 (3): 3832--60.
+\url{https://doi.org/10.1093/mnras/stad2909}.
+
+\bibitem[\citeproctext]{ref-numba:2022}
 Lam, Stan, Stéphane Pitrou, and Mark Seibert. 2022. {``Numba: A High
@@
 
-\bibitem[\citeproctext]{ref-lalsuite}
+\bibitem[\citeproctext]{ref-lalsuite:2018}
 LIGO Scientific Collaboration, Virgo Collaboration, and KAGRA
@@
 
-\bibitem[\citeproctext]{ref-ng2024}
+\bibitem[\citeproctext]{ref-More:2025}
+More, Anupreeta, and Hemantakumar Phurailatpam. 2025. {``Gravitational
+Lensing: Towards Combining the Multi-Messengers.''}
+\url{https://arxiv.org/abs/2502.02536}.
+
+\bibitem[\citeproctext]{ref-Leo:2024}
 Ng, Leo C. Y., Justin Janquart, Hemantakumar Phurailatpam, Harsh Narola,
@@
 
-\bibitem[\citeproctext]{ref-scikitlearn}
+\bibitem[\citeproctext]{ref-numpy:2022}
+NumPy Community. 2022. {``NumPy: A Fundamental Package for Scientific
+Computing with Python.''} \emph{NumPy Website}. NumPy.
+\url{https://numpy.org/}.
+
+\bibitem[\citeproctext]{ref-scikitlearn:2011}
 Pedregosa, Fabian, Gaël Varoquaux, Alexandre Gramfort, Vincent Michel,
@@
 
-\bibitem[\citeproctext]{ref-ler}
+\bibitem[\citeproctext]{ref-gwsnr:documentation}
+Phurailatpam, Hemantakumar, and Otto Akseli Hannuksela. 2025. {``Gwsnr:
+Gravitational Wave Signal-to-Noise Ratio Computation Package
+Documentation.''} \url{https://gwsnr.readthedocs.io/en/latest/}.
+
+\bibitem[\citeproctext]{ref-ler:2024}
 Phurailatpam, Hemantakumar, Anupreeta More, Harsh Narola, Ng Chung Yin,
@@
 
-\bibitem[\citeproctext]{ref-LIGO2015}
+\bibitem[\citeproctext]{ref-LIGO:2015}
 The LIGO Scientific Collaboration, J Aasi, B P Abbott, R Abbott, T
@@
 
+\bibitem[\citeproctext]{ref-Wempe:2022}
+Wempe, Ewoud, Léon V. E. Koopmans, A. Renske A. C. Wierda, Otto Akseli
+Hannuksela, Alberto Agnello, Cyril Bonvin, Bendetta Bucciarelli, et al.
+2022. {``A Lensing Multi-Messenger Channel: Combining LIGO-Virgo-Kagra
+Lensed Gravitational-Wave Measurements with Euclid Observations.''}
+\url{https://arxiv.org/abs/2204.08732}.
+
+\bibitem[\citeproctext]{ref-Wierda:2021}
+Wierda, A. Renske A. C., Ewoud Wempe, Otto A. Hannuksela, Léon V. E.
+Koopmans, Alberto Agnello, Cyril Bonvin, Bendetta Bucciarelli, et al.
+2021. {``Beyond the Detector Horizon: Forecasting Gravitational-Wave
+Strong Lensing.''} \emph{The Astrophysical Journal} 921 (1): 154.
+\url{https://doi.org/10.3847/1538-4357/ac1bb4}.
+
 \end{CSLReferences}

### 2025-06-21 arxiv/paper.tex
mac

@@
 This procedure transforms a computationally intensive integration into a
-simple, JIT-compiled table lookup and multiplication, enabling massive
+simple, JIT-compiled interpolation and multiplication, enabling massive
 performance gains for large-scale population studies.
@@
 No.~PHY-0757058 and No.~PHY-0823459.
+
+\section{References}\label{references}
 

### 2025-06-21 tests/unit/_test_GWSNR_inner_product_jax.py

@@ -12,12 +12,8 @@ def test_gwsnr_snr_generation(tmp_path):
     # Initialize the GWSNR object
     gwsnr = GWSNR(
         npool=4,
-        mtot_min=2.0,
-        mtot_max=439.6,
-        ratio_min=0.1,
-        ratio_max=1.0,
-        mtot_resolution=100,
-        ratio_resolution=20,
+        mtot_resolution=50,
+        ratio_resolution=10,
         sampling_frequency=2048.0,
         waveform_approximant="IMRPhenomXAS",
         minimum_frequency=20.0,

### 2025-06-24 gwsnr/ann/ann_model_generator.py
mac

@@ -13,7 +13,7 @@ from ..numba import (
     antenna_response_array,
 )
 import jax
-jax.config.update("jax_enable_x64", False)
+jax.config.update("jax_enable_x64", True)
 import jax.numpy as jnp
 
 import tensorflow as tf

### 2025-06-24 gwsnr/core/gwsnr.py

@@ -1,9 +1,61 @@
 # -*- coding: utf-8 -*-
 """
-This module contains functions for calculating the SNR of a CBC signal. It has two methods: interpolation (bicubic) and inner product (multiprocessing and jax.jit+jax.vmap). Interpolation method is much faster than inner product method. Interpolation method is tested for IMRPhenomD and TaylorF2 waveform approximants for the spinless scenario.
+gwsnr: A Python package for efficient signal-to-noise ratio (SNR) calculation of gravitational-wave signals from compact binary coalescences (CBCs).
+
+Overview
+--------
+This module provides a flexible and computationally efficient framework to calculate the optimal signal-to-noise ratio (SNR) of gravitational-wave signals for a variety of waveform models and detector configurations. The package supports multiple backend methods for SNR estimation:
+
+1. **Interpolation Method (Partial-Scaled SNR)**:
+   - Implements fast bicubic (and optionally JAX/Numba-accelerated) interpolation of precomputed "partial-scaled" SNRs.
+   - Particularly efficient for aligned-spin or non-spinning systems.
+   - Precomputes a grid of intrinsic parameters (e.g., total mass, mass ratio, aligned spin components) decoupled from extrinsic parameters.
+   - Tested for waveform approximants such as `IMRPhenomD`, `TaylorF2`, and `IMRPhenomXPHM`.
+
+2. **Noise-Weighted Inner Product Method**:
+   - Calculates SNR using the standard inner-product integral between waveform and noise PSD, following the matched-filtering formalism.
+   - Supports multiprocessing and is compatible with waveform generation from `lalsimulation` and `ripple`.
+   - Useful for arbitrary frequency-domain waveform models including precession and higher harmonics.
+
+3. **JAX-based Inner Product**:
+   - Accelerated computation using the `ripple` waveform generator and JAX's `jit` and `vmap` functions for parallelized batched evaluation.
+
+4. **Artificial Neural Network (ANN) Estimation**:
+   - Enables rapid estimation of the probability of detection (`Pdet`) for spin-precessing systems using trained ANN models.
+   - Reduces input dimensionality by leveraging partial-scaled SNR as a summary statistic.
+   - Configurable and extensible with user-supplied ANN models and scalers.
+
+5. **Hybrid SNR Recalculation**:
+   - Combines fast interpolation-based evaluation with inner-product-based recalculation for systems near the SNR detection threshold.
+
+Key Features
+------------
[…]

### 2025-06-24 gwsnr/jax/jaxjit_functions.py

@@ -1,11 +1,34 @@
+# -*- coding: utf-8 -*-
+"""
+JAX-JIT compiled functions for gravitational wave data analysis.
+
+This module provides high-performance JAX implementations of core functions used in 
+gravitational wave signal-to-noise ratio (SNR) calculations and parameter estimation.
+Key features include:
+
+- Chirp time calculations using 3.5 post-Newtonian approximations
+- Antenna response pattern computations for gravitational wave detectors
+- Polarization tensor calculations for plus and cross modes
+- Coordinate transformations between celestial and detector frames
+- Vectorized operations for efficient batch processing
+- Automatic parallelization through JAX's vmap for multi-dimensional arrays
+
+All functions are compiled with JAX's @jit decorator for optimal performance,
+automatic differentiation support, and GPU acceleration. The implementations
+are optimized for use in Bayesian inference pipelines and matched filtering
+applications in gravitational wave astronomy.
+"""
+
 import jax
-jax.config.update("jax_enable_x64", False)
+jax.config.update("jax_enable_x64", True)
 import jax.numpy as jnp
 from jax import jit, vmap
 
 @jit
 def findchirp_chirptime_jax(m1, m2, fmin):
     """
+    Function to calculate the chirp time from minimum frequency to last stable orbit (JAX implementation).
+    
     Time taken from f_min to f_lso (last stable orbit). 3.5PN in fourier phase considered.
 
     Parameters
@@ -15,12 +38,19 @@ def findchirp_chirptime_jax(m1, m2, fmin):
     m2 : `float`
         Mass of the second body in solar masses.
     fmin : `float`
-        Lower frequency cutoff.
+        Lower frequency cutoff in Hz.
 
     Returns
     -------
-    chirp_time : float
-        Time taken from f_min to f_lso (last stable orbit frequency).
+    chirp_time : `float`
+        Time taken from f_min to f_lso (last stable orbit frequency) in seconds.
+
+    Notes
+    -----
+    Calculates chirp time using 3.5PN approximation for gravitational wave Fourier phase.
+    The time represents frequency evolution from fmin to last stable orbit frequency.
+    Uses post-Newtonian expansion coefficients optimized for efficient JAX computation.
+    JAX implementation supports automatic differentiation and GPU acceleration.
     """
 
     Gamma = 0.5772156649015329
@@ -83,16 +113,77 @@ def findchirp_chirptime_jax(m1, m2, fmin):
 
 @jit
[…]

### 2025-06-24 gwsnr/jax/jaxjit_interpolators.py

@@ -1,149 +1,315 @@
+# -*- coding: utf-8 -*-
+
 import jax
-jax.config.update("jax_enable_x64", False)
+jax.config.update("jax_enable_x64", True)
 import jax.numpy as jnp
 from jax import jit, vmap, lax
 from .jaxjit_functions import antenna_response_array
 
 @jit
 def find_index_1d_jax(x_array, x_new):
-    N = x_array.shape[0]
-    i = jnp.sum(x_array <= x_new) - 1
-    i = jnp.clip(i, 1, N - 3)
-    low_lim = x_array[0]+ (x_array[1]-x_array[0]) / 2.0
-    high_lim = x_array[N-2] + (x_array[N-1] - x_array[N-2]) / 2.0
-    
-    condition_0 = x_new <= low_lim
-    condition_1 = (x_new > low_lim) & (x_new <= x_array[1])
-    condition_2 = (x_new > x_array[1]) & (x_new < x_array[N - 2])
-    condition_3 = (x_new >= x_array[N - 2]) & (x_new < high_lim)
-    condition_4 = x_new >= high_lim
+    """
+    Find the index for cubic spline interpolation in 1D.
+    Returns the index and a condition for edge handling.
 
-    condition_i = jnp.where(
-        condition_0, 0,
-        jnp.where(condition_1, 1,
-        jnp.where(condition_2, 2,
-        jnp.where(condition_3, 3, 4))))
-        
+    Parameters
+    ----------
+    x_array : jnp.ndarray
+        The array of x values for interpolation. Must be sorted in ascending order.
+    x_new : float or jnp.ndarray
+        The new x value(s) to find the index for.
+
+    Returns
+    -------
+    i : jnp.ndarray
+        The index in `x_array` where `x_new` would fit, clipped to range [1, N-3] 
+        where N is the length of x_array.
+    condition_i : jnp.ndarray
+        A condition indicating which interpolation branch to use:
+        - 1: Use linear interpolation at the left edge (x_new <= x_array[1]).
+        - 2: Use cubic interpolation in the middle.
+        - 3: Use linear interpolation at the right edge (x_new >= x_array[N-2]).
+
+    Notes
+    -----
+    Uses binary search with clipped indices to ensure valid 4-point stencils.
+    The condition parameter determines linear vs cubic interpolation at boundaries.
+    """
[…]

### 2025-06-24 gwsnr/numba/njit_functions.py

@@ -1,10 +1,21 @@
 # -*- coding: utf-8 -*-
 """
+Numba-compiled helper functions for gravitational wave signal-to-noise ratio calculations.
+
+This module provides optimized numerical functions for gravitational wave data analysis,
+including chirp time calculations, antenna response computations, polarization tensors,
+coordinate transformations, and noise-weighted inner products. All functions are compiled
+with Numba's @njit decorator for high-performance computation, with parallel processing
+support using prange for multi-threaded execution where applicable.
+"""
+
+# -*- coding: utf-8 -*-
+"""
 Helper functions for gwsnr. All functions are njit compiled.
 """
 
 import numpy as np
-from numba import njit
+from numba import njit, prange
 
 Gamma = 0.5772156649015329
 Pi = np.pi
@@ -181,7 +192,7 @@ def ra_dec_to_theta_phi(ra, dec, gmst):
     return theta, phi
 
 @njit
-def get_polarization_tensor(ra, dec, time, psi, mode='plus'):
+def get_polarization_tensor_plus(ra, dec, time, psi):
     """
     Function to calculate the polarization tensor
 
@@ -195,8 +206,6 @@ def get_polarization_tensor(ra, dec, time, psi, mode='plus'):
         GPS time of the source.
     psi : `float`
         Polarization angle of the source.
-    mode : `str`
-        Mode of the polarization. Default is 'plus'.
 
     Returns
     -------
@@ -210,13 +219,40 @@ def get_polarization_tensor(ra, dec, time, psi, mode='plus'):
     m = -u * np.sin(psi) - v * np.cos(psi)
     n = -u * np.cos(psi) + v * np.sin(psi)
 
-    if mode == 'plus':
-        return einsum1(m, m) - einsum1(n, n)
-    elif mode == 'cross':
-        return einsum1(m, n) + einsum1(n, m)
+    return einsum1(m, m) - einsum1(n, n)
+    
+@njit
+def get_polarization_tensor_cross(ra, dec, time, psi):
+    """
+    Function to calculate the polarization tensor
+
+    Parameters
+    ----------
+    ra : `float`
+        Right ascension of the source in radians.
+    dec : float
+        Declination of the source in radians.
+    time : `float`
+        GPS time of the source.
+    psi : `float`
+        Polarization angle of the source.
+
+    Returns
+    -------
+    polarization_tensor: `numpy.ndarray`
[…]

### 2025-06-24 gwsnr/numba/njit_interpolators.py

@@ -2,245 +2,8 @@ import numpy as np
 from numba import njit, prange
 from .njit_functions import antenna_response_array
 
-@njit
-def get_interpolated_snr(mass_1, mass_2, luminosity_distance, theta_jn, psi, geocent_time, ra, dec, detector_tensor, snr_partialscaled, ratio_arr, mtot_arr):
-    """
-    Function to calculate the interpolated snr for a given set of parameters
 
-    Parameters
-    ----------
-    mass_1 : `numpy.ndarray`
-        Mass of the first body in solar masses.
-    mass_2 : `numpy.ndarray`
-        Mass of the second body in solar masses.
-    luminosity_distance : `float`
-        Luminosity distance to the source in Mpc.
-    theta_jn : `numpy.ndarray`
-        Angle between the total angular momentum and the line of sight to the source in radians.
-    psi : `numpy.ndarray`
-        Polarization angle of the source.
-    geocent_time : `numpy.ndarray`
-        GPS time of the source.
-    ra : ``numpy.ndarray`
-        Right ascension of the source in radians.
-    dec : `numpy.ndarray`
-        Declination of the source in radians.
-    detector_tensor : array-like
-        Detector tensor for the detector (3x3 matrix)
-    snr_partialscaled : `numpy.ndarray`
-        Array of snr_partialscaled coefficients for the detector.
-    ratio_arr : `numpy.ndarray`
-        Array of mass ratio values for the snr_partialscaled coefficients.
-    mtot_arr : `numpy.ndarray`
-        Array of total mass values for the snr_partialscaled coefficients.
-    
-    Returns
-    -------
-    snr : `float`
-        snr of the detector.
-    """
-
-    size = len(mass_1)
-    len_ = len(detector_tensor)
-    mtot = mass_1 + mass_2
-    ratio = mass_2 / mass_1
-    # get array of antenna response
-    Fp, Fc = antenna_response_array(ra, dec, geocent_time, psi, detector_tensor)
-
[…]

### 2025-06-24 gwsnr/utils/utils.py

@@ -662,6 +662,7 @@ def interpolator_pickle_path(param_dict_given, path="./interpolator_pickle"):
 
     len_ = len(param_dict_stored)
     # del param_dict_given["psds"]
+    param_dict_given["psds"] = str(param_dict_given["psds"])
     param_dict_given["detector_tensor"] = str(param_dict_given["detector_tensor"])
     # print("\n\n", param_dict_given)
     # print("\n\n",param_dict_stored)

### 2025-06-24 optimized_interpolation.py

@@ -1,0 +1,176 @@
+"""
+Optimized 4D interpolation with pre-computed coefficients
+"""
+import numpy as np
+from numba import njit
+
+@njit
+def precompute_cubic_coefficients_1d(x_array, y_array):
+    """
+    Pre-compute cubic spline coefficients for 1D interpolation.
+    Returns coefficients [a, b, c, d] for each interval.
+    """
+    n = len(x_array)
+    h = np.diff(x_array)
+    
+    # Build tridiagonal system for second derivatives
+    A = np.zeros((n, n))
+    b = np.zeros(n)
+    
+    # Natural spline boundary conditions
+    A[0, 0] = 1.0
+    A[n-1, n-1] = 1.0
+    
+    for i in range(1, n-1):
+        A[i, i-1] = h[i-1]
+        A[i, i] = 2.0 * (h[i-1] + h[i])
+        A[i, i+1] = h[i]
+        b[i] = 3.0 * ((y_array[i+1] - y_array[i]) / h[i] - 
+                      (y_array[i] - y_array[i-1]) / h[i-1])
+    
+    # Solve for second derivatives
+    c = np.linalg.solve(A, b)
+    
+    # Compute coefficients for each interval
+    coeffs = np.zeros((n-1, 4))  # [a, b, c, d] for each interval
+    
+    for i in range(n-1):
+        dx = h[i]
+        coeffs[i, 0] = y_array[i]  # d (constant term)
+        coeffs[i, 1] = (y_array[i+1] - y_array[i]) / dx - dx * (2*c[i] + c[i+1]) / 3.0  # c (linear)
+        coeffs[i, 2] = c[i]  # b (quadratic)
+        coeffs[i, 3] = (c[i+1] - c[i]) / (3.0 * dx)  # a (cubic)
+    
+    return coeffs
+
+@njit
+def fast_cubic_eval(x_eval, x_array, coeffs):
+    """
+    Fast cubic spline evaluation using pre-computed coefficients.
+    """
+    # Find interval
+    i = np.searchsorted(x_array, x_eval, side='right') - 1
+    i = max(0, min(len(coeffs)-1, i))
+    
+    # Evaluate polynomial
+    dx = x_eval - x_array[i]
+    return coeffs[i, 0] + coeffs[i, 1]*dx + coeffs[i, 2]*dx*dx + coeffs[i, 3]*dx*dx*dx
+
+@njit
[…]

### 2025-06-24 setup.py

@@ -32,7 +32,7 @@ setup(
     url='https://github.com/hemantaph/gwsnr',
     packages=find_packages(),
     package_data={
-        'gwsnr': ['ann/data/*.json', 'ann/data/*.pkl', 'ann/data/*.h5'],
+        'gwsnr': ['ann/data/*.json', 'ann/data/*.pkl', 'ann/data/*.h5', 'core/interpolator_pickle/'],
     },
     install_requires=requirements,
 )

### 2025-06-24 tests/integration/_test_Pdet_BBH_aligned_spin.py

@@ -1,67 +1,0 @@
-'''
-Generate SNR for 10 random BBH events (with aligned spin) and save it to a json file.
-Use detectors L1, H1, V1 with O4 design sensitivity
-'''
-
-import numpy as np
-from gwsnr import GWSNR
-from gwsnr.utils import append_json
-import pytest
-np.random.seed(1234)
-
-def test_gwsnr_snr_generation(tmp_path):
-    # Initialize the GWSNR object
-    gwsnr = GWSNR(
-        npool=4,
-        mtot_resolution=100,
-        ratio_resolution=20,
-        waveform_approximant="IMRPhenomXPHM",
-        snr_type="ann",
-        ifos=["L1", "H1", "V1"],
-        interpolator_dir="./interpolator_pickle",
-        pdet=True,
-        create_new_interpolator=False,
-        gwsnr_verbose=False,
-        multiprocessing_verbose=False,
-    )
-
-    # Generate BBH parameters
-    nsamples = 10
-    chirp_mass = np.linspace(5,60,nsamples)
-    mass_ratio = np.random.uniform(0.2,1,size=nsamples)
-    param_dict = dict(
-        mass_1 = (chirp_mass*(1+mass_ratio)**(1/5))/mass_ratio**(3/5),
-        mass_2 = chirp_mass*mass_ratio**(2/5)*(1+mass_ratio)**(1/5),
-        # Fix luminosity distance
-        luminosity_distance = 500*np.ones(nsamples),
-        # Randomly sample everything else:
-        theta_jn = np.random.uniform(0,2*np.pi, size=nsamples),
-        ra = np.random.uniform(0,2*np.pi, size=nsamples), 
-        dec = np.random.uniform(0,np.pi, size=nsamples), 
-        psi = np.random.uniform(0,2*np.pi, size=nsamples),
-        phase = np.random.uniform(0,2*np.pi, size=nsamples),
-        geocent_time = 1246527224.169434*np.ones(nsamples),
-        # spin non-zero
-        a_1 = np.random.uniform(0,0.8, size=nsamples),
-        a_2 = np.random.uniform(0,0.8, size=nsamples),
-        tilt_1 = np.zeros(nsamples),
-        tilt_2 = np.zeros(nsamples),
-        phi_12 = np.zeros(nsamples),
-        phi_jl = np.zeros(nsamples),
-    )
-
-    # Calculate SNR
-    interp_snr = gwsnr.snr(
-        gw_param_dict=param_dict
-    )
-
[…]

### 2025-06-24 tests/integration/_test_SNR_BBH_precessing_spin.py

@@ -1,64 +1,0 @@
-'''
-Generate SNR for 10 random BBH events (with precessing spin) and save it to a json file.
-Use detectors L1, H1, V1 with O4 design sensitivity
-'''
-
-import numpy as np
-from gwsnr import GWSNR
-from gwsnr.utils import append_json
-import pytest
-np.random.seed(1234)
-
-def test_gwsnr_snr_generation(tmp_path):
-    # Initialize the GWSNR object
-    gwsnr = GWSNR(
-        npool=4,
-        waveform_approximant="IMRPhenomXPHM",
-        snr_type="inner_product",
-        ifos=["L1", "H1", "V1"],
-        interpolator_dir="./interpolator_pickle",
-        create_new_interpolator=False,
-        gwsnr_verbose=False,
-        multiprocessing_verbose=False,
-    )
-
-    # Generate BBH parameters
-    nsamples = 10
-    chirp_mass = np.linspace(5,60,nsamples)
-    mass_ratio = np.random.uniform(0.2,1,size=nsamples)
-    param_dict = dict(
-        mass_1 = (chirp_mass*(1+mass_ratio)**(1/5))/mass_ratio**(3/5),
-        mass_2 = chirp_mass*mass_ratio**(2/5)*(1+mass_ratio)**(1/5),
-        # Fix luminosity distance
-        luminosity_distance = 500*np.ones(nsamples),
-        # Randomly sample everything else:
-        theta_jn = np.random.uniform(0,2*np.pi, size=nsamples),
-        ra = np.random.uniform(0,2*np.pi, size=nsamples), 
-        dec = np.random.uniform(0,np.pi, size=nsamples), 
-        psi = np.random.uniform(0,2*np.pi, size=nsamples),
-        phase = np.random.uniform(0,2*np.pi, size=nsamples),
-        geocent_time = 1246527224.169434*np.ones(nsamples),
-        # spin non-zero
-        a_1 = np.random.uniform(0,0.8, size=nsamples),
-        a_2 = np.random.uniform(0,0.8, size=nsamples),
-        tilt_1 = np.random.uniform(0,np.pi, size=nsamples),
-        tilt_2 = np.random.uniform(0,np.pi, size=nsamples),
-        phi_12 = np.random.uniform(0,2*np.pi, size=nsamples),
-        phi_jl = np.random.uniform(0,2*np.pi, size=nsamples),
-    )
-
-    # Calculate SNR
-    interp_snr = gwsnr.snr(
-        gw_param_dict=param_dict
-    )
-
[…]

### 2025-06-24 tests/integration/test_Pdet_BBH_aligned_spin.py

@@ -1,0 +1,67 @@
+'''
+Generate SNR for 10 random BBH events (with aligned spin) and save it to a json file.
+Use detectors L1, H1, V1 with O4 design sensitivity
+'''
+
+import numpy as np
+from gwsnr import GWSNR
+from gwsnr.utils import append_json
+import pytest
+np.random.seed(1234)
+
+def test_gwsnr_snr_generation(tmp_path):
+    # Initialize the GWSNR object
+    gwsnr = GWSNR(
+        npool=4,
+        mtot_resolution=100,
+        ratio_resolution=20,
+        waveform_approximant="IMRPhenomXPHM",
+        snr_type="ann",
+        ifos=["L1", "H1", "V1"],
+        interpolator_dir="./interpolator_pickle",
+        pdet=True,
+        create_new_interpolator=False,
+        gwsnr_verbose=False,
+        multiprocessing_verbose=False,
+    )
+
+    # Generate BBH parameters
+    nsamples = 10
+    chirp_mass = np.linspace(5,60,nsamples)
+    mass_ratio = np.random.uniform(0.2,1,size=nsamples)
+    param_dict = dict(
+        mass_1 = (chirp_mass*(1+mass_ratio)**(1/5))/mass_ratio**(3/5),
+        mass_2 = chirp_mass*mass_ratio**(2/5)*(1+mass_ratio)**(1/5),
+        # Fix luminosity distance
+        luminosity_distance = 500*np.ones(nsamples),
+        # Randomly sample everything else:
+        theta_jn = np.random.uniform(0,2*np.pi, size=nsamples),
+        ra = np.random.uniform(0,2*np.pi, size=nsamples), 
+        dec = np.random.uniform(0,np.pi, size=nsamples), 
+        psi = np.random.uniform(0,2*np.pi, size=nsamples),
+        phase = np.random.uniform(0,2*np.pi, size=nsamples),
+        geocent_time = 1246527224.169434*np.ones(nsamples),
+        # spin non-zero
+        a_1 = np.random.uniform(0,0.8, size=nsamples),
+        a_2 = np.random.uniform(0,0.8, size=nsamples),
+        tilt_1 = np.zeros(nsamples),
+        tilt_2 = np.zeros(nsamples),
+        phi_12 = np.zeros(nsamples),
+        phi_jl = np.zeros(nsamples),
+    )
+
+    # Calculate SNR
+    interp_snr = gwsnr.snr(
+        gw_param_dict=param_dict
+    )
+
[…]

### 2025-06-24 tests/integration/test_SNR_BBH_non_spinning.py

@@ -13,8 +13,6 @@ def test_gwsnr_snr_generation(tmp_path):
     # Initialize the GWSNR object
     gwsnr = GWSNR(
         npool=4,
-        mtot_resolution=100,
-        ratio_resolution=20,
         waveform_approximant="IMRPhenomD",
         minimum_frequency=20.0,
         snr_type="interpolation",

### 2025-06-24 tests/unit/test_GWSNR_interpolation.py

@@ -1,0 +1,175 @@
+import numpy as np
+import pytest
+from gwsnr import GWSNR
+from gwsnr.utils import append_json
+
+np.random.seed(1234)
+
+class TestGWSNRInterpolation:
+    """
+    Unit tests for the GWSNR interpolation-based SNR calculation.
+    """
+
+    def test_default_snr_generation(self, tmp_path):
+        """
+        Test SNR generation with default GWSNR interpolation settings.
+        """
+        gwsnr = GWSNR(
+            npool=int(4),
+            mtot_min=2.0,
+            mtot_max=439.6,
+            ratio_min=0.1,
+            ratio_max=1.0,
+            spin_max=0.9,
+            mtot_resolution=200,
+            ratio_resolution=50,
+            spin_resolution=20,
+            sampling_frequency=2048.0,
+            waveform_approximant="IMRPhenomD",
+            frequency_domain_source_model='lal_binary_black_hole',
+            minimum_frequency=20.0,
+            duration_max=None,
+            duration_min=None,
+            snr_type="interpolation",
+            psds=None,
+            ifos=None,
+            interpolator_dir="./interpolator_pickle",
+            create_new_interpolator=False,
+            gwsnr_verbose=True,
+            multiprocessing_verbose=True,
+            mtot_cut=True,
+            pdet=False,
+            snr_th=8.0,
+            snr_th_net=8.0,
+            ann_path_dict=None,
+            snr_recalculation=False,
+            snr_recalculation_range=[6,8],
+            snr_recalculation_waveform_approximant="IMRPhenomXPHM",
+        )
+
+        nsamples = 10
+        chirp_mass = np.linspace(5, 60, nsamples)
+        mass_ratio = np.random.uniform(0.2, 1, size=nsamples)
+        param_dict = dict(
+            mass_1=(chirp_mass * (1 + mass_ratio) ** (1 / 5)) / mass_ratio ** (3 / 5),
+            mass_2=chirp_mass * mass_ratio ** (2 / 5) * (1 + mass_ratio) ** (1 / 5),
+            luminosity_distance=500 * np.ones(nsamples),
+            theta_jn=np.random.uniform(0, 2 * np.pi, size=nsamples),
+            ra=np.random.uniform(0, 2 * np.pi, size=nsamples),
+            dec=np.random.uniform(0, np.pi, size=nsamples),
+            psi=np.random.uniform(0, 2 * np.pi, size=nsamples),
[…]
